### 2018-05-12 paper/paper.tex
Start paper outline

\documentclass[11 pt]{extarticle}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsthm,amssymb}
\usepackage[shortlabels, inline]{enumitem}
\usepackage{mleftright}
\usepackage{array}
\usepackage{gensymb}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{pgfplots}
\usepackage{booktabs}
\usepackage[numbers]{natbib}
\usepackage{todonotes}
\newcommand\mdoubleplus{\mathbin{+\mkern-10mu+}}
\usepackage{tikz-cd}
% http://tex.stackexchange.com/q/169557/5764
\usepackage{mathtools}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\newcommand{\vectorproj}[2][]{\textit{proj}_{\vect{#1}}\vect{#2}}
\newcommand{\vect}{\mathbf}
\pgfplotsset{width=10cm,compat=1.9}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Mat}{\text{Mat}}
\newcommand{\sgn}{\text{sgn}}
\DeclareMathOperator{\lcm}{lcm}
\DeclareMathOperator{\img}{im}

\let\hom\relax% Set equal to \relax so that LaTeX thinks it's not defined
\DeclareMathOperator{\hom}{Hom}
\newcommand{\Char}{\text{char}}
\newcommand{\defeq}{\overset{\text{\tiny def}}{=}}

\theoremstyle{remark}
\newtheorem{lemma}{Lemma}

\newenvironment{amatrix}[1]{%
  \left[\begin{array}{@{}*{#1}{c}|c@{}}
          }{%
        \end{array}\right]
    }

    \renewcommand\qedsymbol{$\blacksquare$}

    \newenvironment{theorem}[2][Theorem]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
    \newenvironment{theorem*}[1][Theorem:]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
    \newenvironment{exercise}[2][Exercise]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
    \newenvironment{reflection}[2][Reflection]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
    \newenvironment{proposition}[2][Proposition]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
    \newenvironment{corollary}[2][Corollary]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

    \begin{document}
    \onehalfspacing

    \title{Zero-Knowledge Credentials for Smart Contracts}
    \author{Lucas Switzer, Tjaden Hess}

    \maketitle

    \begin{abstract}
      Public blockchains present unique opportunities for the implementation of
      autonomous and trustless systems, but suffer from trade-offs between
      privacy and expressivity. In this paper we present an implementation of a
      zkSNARK-based
      anonymous credential scheme for the Ethereum blockchain and give
      benchmarks for usage costs. We present as well an example application.
    \end{abstract}

    \section{Introduction}
    While blockchains have found use cases in publicly accessible distributed
    systems, they pose a challenge in that due to their public nature it is
    currently impossible to attest to aspects of one's identity without some
    trusted credential issuer.

    \subsection{Prior Work}
    A generalized scheme was proposed by \citet{garmanDecentralizedAnonymousCredentials2013}

    \section{Properties and Features}

    \section{Implementation}

    \section{Benchmarks}

    \section{Example Application}

    \section{Future Work}

    \section{Conclusion}

    \bibliographystyle{plainnat}
    \bibliography{Identity}
  \end{document}

### 2018-05-12 include/proving/zkidMTA.h
Compilation fixes

@@ -33,19 +33,20 @@ struct MTAuthenticationNode
     MTAuthenticationNode(){};
 };
 
-template<typename FieldT>
 struct ProofRequest {
   std::string secret_key;
   std::string merkle_root;
   std::vector<MTAuthenticationNode> path;
 
-  std::array<std::string, 7> attributes;
-  std::array<std::string, 7> upper_bounds;
-  std::array<std::string, 7> lower_bounds;
+  std::string attributes;
+  std::string upper_bounds;
+  std::string lower_bounds;
   unsigned long k_bound;
   unsigned long k;
   std::string salt;
 };
+
+void ProofRequestFromJson(const std::string &path, ProofRequest &proof);
 
 template <template <typename> typename Hash>
 class zkID : public zkidProofGadget
@@ -61,7 +62,7 @@ class zkID : public zkidProofGadget
 
     typedef Hash<FieldT> HashT;
 
-    bool GetVerificationData(ProofRequest<FieldT> &proof_req, VerificationData &data,
+    bool GetVerificationData(ProofRequest &proof_req, VerificationData &data,
                              LibsnarkVerificationData *libsnark_data = nullptr)
     {
         //Pb variables
@@ -73,7 +74,7 @@ class zkID : public zkidProofGadget
         libff::bit_vector attributes_bv(attribute_size*7);
         libff::bit_vector lower_bounds_bv(attribute_size*7);
         libff::bit_vector upper_bounds_bv(attribute_size*7);
-        libff::bit_vector salt_bv(FieldT::capacity-32);
+        libff::bit_vector salt_bv(FieldT::capacity()-32);
         std::vector<libsnark::merkle_authentication_node> auth_path(tree_depth);
         size_t address = 0;
 
@@ -84,30 +85,20 @@ class zkID : public zkidProofGadget
         bit_vector_from_string(root_hash_bv, proof_req.merkle_root);
         bit_vector_from_string(salt_bv, proof_req.salt);
         bit_vector_from_string(secret_key_bv, proof_req.secret_key);
-        // Construct attribute strings
-        for (int i = 0; i < 7; i++){
-          libff::bit_vector attribute(attribute_size);
-          libff::bit_vector upper(attribute_size);
-          libff::bit_vector lower(attribute_size);
-          bit_vector_from_string(attribute, proof_req.attributes[i]);
-          bit_vector_from_string(upper, proof_req.upper_bounds[i]);
[…]

### 2018-05-12 include/proving/zkidMTACircuit.h

@@ -25,9 +25,9 @@ private:
 public:
     zkrange_gadget(protoboard<FieldT> &pb,
                    size_t n,
-                   pb_linear_combination<FieldT> &upper_bound,
-                   pb_linear_combination<FieldT> &lower_bound,
-                   pb_linear_combination<FieldT> &attribute)
+                   const pb_linear_combination<FieldT> &upper_bound,
+                   const pb_linear_combination<FieldT> &lower_bound,
+                   const pb_linear_combination<FieldT> &attribute)
         : gadget<FieldT>(pb), attribute(attribute)
         {
             // Generate dummy variables for LT, we only care about LE
@@ -37,10 +37,10 @@ public:
             lt2.allocate(pb);
 
             // Constrain `attribute <= upper_bound`
-            upper.reset(new comparison_gadget<FieldT>(n, attribute, upper_bound, lt1, ONE));
+            upper.reset(new comparison_gadget<FieldT>(pb, n, attribute, upper_bound, lt1, ONE));
 
             //Constrain `lower_bound <= attribute`
-            lower.reset(new comparison_gadget<FieldT>(n, lower_bound, lt2, ONE));
+            lower.reset(new comparison_gadget<FieldT>(pb, n, lower_bound, attribute, lt2, ONE));
         }
     void generate_r1cs_constraints(){
         upper->generate_r1cs_constraints();
@@ -191,15 +191,16 @@ class zkid_gadget : gadget<FieldT> {
   pb_variable_array<FieldT> lower_bounds_split;
 
   // Hash inputs
-  block_variable<FieldT> serial_inputs;
-  block_variable<FieldT> leaf_inputs;
+  std::shared_ptr<block_variable<FieldT>> serial_inputs;
+  std::shared_ptr<block_variable<FieldT>> leaf_inputs;
 
 
- zkid_gadget(protoboard<FieldT> &pb,
-             size_t tree_depth,
-             size_t attribute_size) :
-  gadget<FieldT>(pb)
-    {
+ zkid_gadget(protoboard<FieldT> &pb, size_t tree_depth, size_t attribute_size) :
+  gadget<FieldT>(pb),
+    leaf_digest(pb, HashT::get_digest_len(), "leaf"),
+    merkle_root_digest(pb, HashT::get_digest_len(), "root"),
+    serial_number_digest(pb, HashT::get_digest_len(), "serial")
+   {
       size_t digest_len = HashT::get_digest_len();
[…]

### 2018-05-12 test/authentication/zkMerkelTreeAuthenticatorTest.cpp

@@ -4,7 +4,7 @@
 #include "proving/zkidMTA.h"
 #include "util/zkid_helpers.h"
 
-//
+
 #define M_TREE_LENGTH 3
 
 TEST(zkMTATest, TestProofGenerationPbSatisfaction){
@@ -69,6 +69,14 @@ TEST(zkMTATest, TestVerifyFail){
   ASSERT_FALSE(verified);
 }
 
+
 TEST(zkIDTest, TestProofGeneration){
-  
+  ProofRequest proof;
+  VerificationData verification_data;
+
+  ProofRequestFromJson("test/res/credentials/test_credential_proof.json", proof);
+  libff::alt_bn128_pp::init_public_params();
+  zkID<sha256_two_to_one_hash_gadget> authenticator(proof.path.size(), 32);
+  bool verifiable = authenticator.GetVerificationData(proof, verification_data);
+  ASSERT_TRUE(verifiable);
 }

### 2018-05-12 include/credentials/CredentialsManager.h
Added proof parsing to verifier contract

@@ -8,9 +8,23 @@
 
 struct Credential{
     Credential(){};
-    Credential(uint32_t t, size_t a) : token(t), address(a){};
-    uint32_t token;
-    size_t address;
+    Credential(std::string a, std::string l, std::string u, int kb, int _k, std::string cs, 
+        std::string sn,uint ma) : attributes(a), 
+                                          lower_bound(l),
+                                          upper_bound(u),
+                                          k(_k),
+                                          k_bound(kb),
+                                          contract_salt(cs),
+                                          serial_number(sn),
+                                          merkle_address(ma){};
+    std::string attributes;
+    std::string lower_bound;
+    std::string upper_bound;
+    int k_bound;
+    int k;
+    std::string contract_salt;
+    std::string serial_number;
+    uint merkle_address;
 };
 
 class CredentialsManager{

### 2018-05-12 include/proving/zkidVerificationStructs.h

@@ -12,11 +12,11 @@ enum VerificationErrorCode
 };
 
 struct CredentialRequest{
-  std::string issuer_address;
+  std::string contract_salt;
   std::string merkle_root_address;
-  uint32_t range_low;
-  uint32_t range_high;
-  uint32_t k_factor;
+  std::string lower_bound;
+  std::string upper_bound;
+  int k_bound;
 };
 
 struct CredentialProof

### 2018-05-12 src/credentials/CredentialsManager.cpp

@@ -9,12 +9,18 @@ Credential CredentialsManager::GetCredential(const std::string& issuer_address){
 }
 
 void CredentialsManager::LoadCredentials(){
-    const std::string& credentials_directory = _cred_config->GetCredentialsFilePath();
+    const std::string& credential_file = _cred_config->GetCredentialsFilePath();
 
-    Json::Value creds_json = JsonObjectFromFile(credentials_directory);
+    Json::Value creds_json = JsonObjectFromFile(credential_file);
 
     for(int i = 0; i < creds_json.size(); i++){
         Json::Value current_cred = creds_json[i];
-        _credentials[current_cred["issuer_address"].asString()] = Credential(current_cred["token"].asInt(), current_cred["address"].asInt());
-    }
+        _credentials[current_cred["contract_salt"].asString()] = Credential(current_cred["attributes"].asString(), 
+                                                                            current_cred["lower_bound"].asString(),
+                                                                            current_cred["upper_bound"].asString(),
+                                                                            current_cred["k_bound"].asInt(),
+                                                                            current_cred["k"].asInt(),
+                                                                            current_cred["contract_salt"].asString(),
+                                                                            current_cred["serial_number"].asString(),
+                                                                            current_cred["merkel_address"].asInt());}
 }

### 2018-05-12 src/network/ZkidRPCServer.cpp

@@ -25,7 +25,7 @@ Json::Value ZkidRPCServer::GenerateProofs(const Json::Value &credential_descs)
         if (_proof_handler->GetProofForCredential(cred, proof))
         {
             Json::Value proof_json = ProofToJson(proof);
-            proof_json["issuer_address"] = cred.issuer_address;
+            proof_json["contract_salt"] = cred.contract_salt;
             result["proofs"].append(proof_json);
         }
     }
@@ -37,11 +37,11 @@ Json::Value ZkidRPCServer::GenerateProofs(const Json::Value &credential_descs)
 CredentialRequest ZkidRPCServer::CredentialRequestFromJson(const Json::Value &cred_json)
 {
     CredentialRequest cred_desc;
-    cred_desc.issuer_address = cred_json["issuer_address"].asString();
+    cred_desc.contract_salt = cred_json["contract_salt"].asString();
     cred_desc.merkle_root_address = cred_json["merkle_root_address"].asString();
-    cred_desc.range_low = cred_json["range_low"].asInt();
-    cred_desc.range_high = cred_json["range_high"].asInt();
-    cred_desc.k_factor = cred_json["k_factor"].asInt();
+    cred_desc.lower_bound = cred_json["lower_bound"].asString();
+    cred_desc.upper_bound = cred_json["upper_bound"].asString();
+    cred_desc.k_bound = cred_json["k_bound"].asInt();
 
     return cred_desc;
 }

### 2018-05-12 src/network/ZkidService.cpp

@@ -31,8 +31,8 @@ bool ZkidService::GetProofForCredential(const CredentialRequest &cred, Credentia
         merkle_root_address: {1} \n \
         range_low: {2} \n \
         range_high: {3} \n \
-        k_factor: {4}",
-                  cred.issuer_address, cred.merkle_root_address, cred.range_low, cred.range_high, cred.k_factor);
+        k_bound: {4}",
+                  cred.contract_salt, cred.merkle_root_address, cred.lower_bound, cred.upper_bound, cred.k_bound);
 
     return GenerateProofForCredential(cred, proof);
 }
@@ -46,7 +46,7 @@ bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_reque
 {
     zkidProver prover(_service_config);
 
-    const std::string issuer_address = cred_request.issuer_address;
+    const std::string issuer_address = cred_request.contract_salt;
     if (!_cred_manager->HasCredential(issuer_address))
     {
         return false;
@@ -54,6 +54,6 @@ bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_reque
 
     Credential cred = _cred_manager->GetCredential(issuer_address);
     std::vector<std::string> merkle_path;
-    _mt_provider->GetMerklePath(cred_request.merkle_root_address,cred.address,merkle_path);
+    _mt_provider->GetMerklePath(cred_request.merkle_root_address,cred.merkle_address,merkle_path);
     return prover.GenerateProof(cred, cred_request, merkle_path, proof);
 }

### 2018-05-12 src/ui/js/credentials.js

@@ -3,7 +3,7 @@ issuer_abi = JSON.parse('[{"constant":false,"inputs":[],"name":"getMerkleRootAdd
 IssuerContract = web3.eth.contract(issuer_abi);
 currentBlock = null;
 
-function ProofToBytes(proof) {
+function ProofToBytes(proof, publicInputs) {
     return [].concat(
         web3.utils.hexToBytes(proof["A"][0]),
         web3.utils.hexToBytes(proof["A"][1]),
@@ -23,6 +23,8 @@ function ProofToBytes(proof) {
         web3.utils.hexToBytes(proof["H"][1]),
         web3.utils.hexToBytes(proof["K"][0]),
         web3.utils.hexToBytes(proof["K"][1]));
+
+        //TODO: Append public inputs
 }
 
 
@@ -57,7 +59,7 @@ CredentialBlock.prototype.FetchCredentialProofs = function () {
             var proof_bytes = generated_proofs.reduce(function (acc, e) {
                 acc.concat(ProofToBytes(e));
             }, []);
-            action.method(proof_bytes);
+            action.method(proof_bytes,generated_proofs.length);
         } else {
             $("#msg-container").first().text("A proof could not be generated for one or more credentials.");
             $("#msg-container").show();

### 2018-05-12 src/ui/js/site.js

@@ -12,7 +12,7 @@ function OnJoinClick() {
 /* Use partial application to supply non-proof arguments */
 
 function PartialAppJoin(/* Insert non-proof arguments here*/) {
-    return function (proof_bytes) {
-        contractInstance.methods["Join"](proof_bytes).send();
+    return function (proof_bytes, numOfProofs) {
+        contractInstance.methods["Join"](proof_bytes,numOfProofs).send();
     }
 }

### 2018-05-12 include/credentials/CredentialsManager.h
IPFS excepctions and credentials test

@@ -17,13 +17,13 @@ struct Credential{
                                           contract_salt(cs),
                                           serial_number(sn),
                                           merkle_address(ma){};
-    std::string attributes;
+    std::string contract_salt;
     std::string lower_bound;
     std::string upper_bound;
     int k_bound;
-    int k;
-    std::string contract_salt;
     std::string serial_number;
+    std::string attributes;
+    int k;
     uint merkle_address;
 };
 

### 2018-05-12 run_service.cpp

@@ -20,16 +20,21 @@ int main(int argc, char **argv)
     try
     {
         ZkidService service(&config, &cred_manager, &zkidIPFSGateway);
+
+        service.console->info("Loading user credentials from: {0}",config.GetCredentialsFilePath());
+        cred_manager.LoadCredentials();
+
         if (result["l"].as<bool>())
         {
             service.console->info("Starting IPFS daemon...", service.GetPort());
-            ipfs_service.StartService(argv);
+            ipfs_service.StartService();
         }
         if (service.Start())
         {
             service.console->info("Started zkid service on port {0} successfully!", service.GetPort());
             getchar();
             service.Stop();
+            ipfs_service.StopService();
         }
         else
         {

### 2018-05-12 src/network/IPFSServiceController.cpp

@@ -2,6 +2,10 @@
 
 void IPFSServiceController::StartService(char** argv)
 {
+    if(!argv){
+        argv =  new char*[3]{"/usr/local/bin/ipfs", "daemon", NULL};
+    }
+
     pid_t pid = fork();
     if (pid == 0)
     {
@@ -12,6 +16,8 @@ void IPFSServiceController::StartService(char** argv)
     {
         this->_ipfs_process_id = pid;
     }
+
+    free(argv);
 }
 
 void IPFSServiceController::StopService()

### 2018-05-12 src/network/ZkidService.cpp

@@ -29,8 +29,8 @@ bool ZkidService::GetProofForCredential(const CredentialRequest &cred, Credentia
     console->info("Recieved request for proof of credential: \n \
         issuer_address: {0} \n \
         merkle_root_address: {1} \n \
-        range_low: {2} \n \
-        range_high: {3} \n \
+        lower_bound: {2} \n \
+        upper_bound: {3} \n \
         k_bound: {4}",
                   cred.contract_salt, cred.merkle_root_address, cred.lower_bound, cred.upper_bound, cred.k_bound);
 
@@ -49,11 +49,18 @@ bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_reque
     const std::string issuer_address = cred_request.contract_salt;
     if (!_cred_manager->HasCredential(issuer_address))
     {
+        console->error("User does not have a credential from: {0}",issuer_address);
         return false;
     }
 
     Credential cred = _cred_manager->GetCredential(issuer_address);
     std::vector<std::string> merkle_path;
     _mt_provider->GetMerklePath(cred_request.merkle_root_address,cred.merkle_address,merkle_path);
+
+    if(merkle_path.empty()){
+        console->error("Enable to get merkle path from: {0}",cred_request.merkle_root_address);
+        return false;
+    }
+
     return prover.GenerateProof(cred, cred_request, merkle_path, proof);
 }

### 2018-05-12 src/network/zkidIPFSGateway.cpp

@@ -11,33 +11,41 @@ void zkidIPFSGateway::GetMerklePath(const std::string &merkle_address, size_t ad
      * the root.
      */
 
-    ipfs::Json parent;
-    _client.ObjectGet(merkle_address, &parent);
-
-    ipfs::Json links = parent["Links"];
-    if (links.size() == 0)
-        return; //hit leafs
-    ipfs::Json left_addr = links[0]["Hash"];
-    ipfs::Json right_addr = links[1]["Hash"];
-
-    ipfs::Json path_element_hash;
-    ipfs::Json next_parent;
-
-    if (address & (1 << path.size()))
+    try
     {
-        path_element_hash = left_addr;
-        next_parent = right_addr;
-    }
-    else
-    {
-        path_element_hash = right_addr;
-        next_parent = left_addr;
-    }
 
-    ipfs::Json path_element;
-    _client.ObjectGet(path_element_hash, &path_element);
-    path.push_back(path_element["Data"]);
-    GetMerklePath(next_parent, address, path);
+        ipfs::Json parent;
+        _client.ObjectGet(merkle_address, &parent);
+
+        ipfs::Json links = parent["Links"];
+        if (links.size() == 0)
+            return; //hit leafs
+        ipfs::Json left_addr = links[0]["Hash"];
+        ipfs::Json right_addr = links[1]["Hash"];
+
+        ipfs::Json path_element_hash;
+        ipfs::Json next_parent;
+
+        if (address & (1 << path.size()))
+        {
+            path_element_hash = left_addr;
+            next_parent = right_addr;
+        }
+        else
+        {
+            path_element_hash = right_addr;
+            next_parent = left_addr;
+        }
+
+        ipfs::Json path_element;
+        _client.ObjectGet(path_element_hash, &path_element);
+        path.push_back(path_element["Data"]);
+        GetMerklePath(next_parent, address, path);
+
+    }catch(std::runtime_error& e){
+        //unable to get files
+        path.clear();
+    }
 }
 
 std::string zkidIPFSGateway::PutMerkleTree(const std::vector<std::string> &tree, int i)

### 2018-05-12 src/ui/js/site.js

@@ -1,5 +1,5 @@
 web3 = new Web3(new Web3.providers.HttpProvider("http://localhost:8545"));
-lottery_abi = JSON.parse('[{"constant":false,"inputs":[],"name":"Join","outputs":[],"payable":false,"type":"function","credentials":[{"issuer_address":"0xdeadbeef","range_high":0,"range_low":0,"k_factor":0,"description":"Confirms holder is over 18."},{"issuer_address":"0xfeedbeef","range_high":0,"range_low":0,"k_factor":0,"description":"Confirms holder is American."}]}]')
+lottery_abi = JSON.parse('[{"constant":false,"inputs":[{"indexed": false,"name": "proofs","type": "uint[]"}],"name":"Join","outputs":[],"payable":false,"type":"function","credentials":[{"contract_salt":"0xdeadbeef","upper_bound":0,"lower_bound":0,"k_bound":0,"description":"Confirms holder is over 18."},{"contract_salt":"0xbeefdead","upper_bound":100,"lower_bound":18,"k_bound":1,"description":"Confirms holder is American."}]}]')
 
 LotteryContract = web3.eth.contract(lottery_abi);
 contractInstance = LotteryContract.at("CONTRACT_ADDR");

### 2018-05-12 src/ui/js/zkid.js

@@ -94,7 +94,7 @@ CredentialBlock.prototype.display = function () {
             var current_cred = requiredCredentials[i];
             var cred_row = document.createElement("tr");
             var cred_sig_cell = document.createElement("td");
-            var cred_sig = document.createTextNode(current_cred["issuer_address"]);
+            var cred_sig = document.createTextNode(current_cred["contract_salt"]);
             var cred_desc_cell = document.createElement("td");;
             var cred_desc = document.createTextNode(current_cred["description"]);
 

### 2018-05-13 include/proving/zkidMTA.h
Fix sgfaults

@@ -55,8 +55,9 @@ class zkID : public zkidProofGadget
  zkID(int tree_depth, int attribute_size) : _zkid(_pb, tree_depth, attribute_size), attribute_size(attribute_size)
     {
       _zkid.generate_r1cs_constraints();
+      auto cs = _pb.get_constraint_system();
       _keypair = std::make_shared<r1cs_ppzksnark_keypair<ppt>>
-        (r1cs_ppzksnark_keypair<ppt>(r1cs_ppzksnark_generator<ppt>(_pb.get_constraint_system())));
+        (r1cs_ppzksnark_keypair<ppt>(r1cs_ppzksnark_generator<ppt>(cs)));
       _verification_key = r1cs_ppzksnark_verification_key<ppt>(_keypair->vk);
     };
 
@@ -101,7 +102,7 @@ class zkID : public zkidProofGadget
                                     root_hash_bv,
                                     address,
                                     auth_path);
-
+        printf("HERE4\n");
         //Generate a authentication proof if the pb is satisified.
         if (!_pb.is_satisfied())
             return false;

### 2018-05-13 include/proving/zkidMTACircuit.h

@@ -161,6 +161,8 @@ class zkid_gadget : gadget<FieldT> {
   std::shared_ptr<merkle_tree_check_read_gadget<FieldT, HashT>> merkle_check;
 
  public:
+  pb_variable<FieldT> ZERO;
+
   pb_variable_array<FieldT> upper_bounds_bits;
   pb_variable_array<FieldT> lower_bounds_bits;
   pb_variable_array<FieldT> attributes_split;
@@ -214,12 +216,11 @@ class zkid_gadget : gadget<FieldT> {
       salt_kbound_packed.allocate(pb);
 
       pb.set_input_sizes(5);
-
+      ZERO.allocate(pb);
       private_key.allocate(pb, digest_len);
-
+      
       // pack as many attributes as fit into a single field element
       size_t num_attributes = FieldT::capacity()/attribute_size;
-
       // unpack bounds arrays into single field elements
       upper_bounds_bits.allocate(pb, num_attributes*attribute_size);
       upper_bounds_split.allocate(pb, num_attributes);
@@ -230,6 +231,8 @@ class zkid_gadget : gadget<FieldT> {
       lower_bounds_split.allocate(pb, num_attributes);
       lower_splitter.reset(new multipacking_gadget<FieldT>(pb, lower_bounds_bits, lower_bounds_split, attribute_size));
       bit_packers.emplace_back(new packing_gadget<FieldT>(pb, lower_bounds_bits, lower_bound_packed));
+
+      attributes_split.allocate(pb, num_attributes);
 
       // constrain each attribute to be in-bounds
       for(int i = 0; i < num_attributes; ++i)
@@ -244,6 +247,7 @@ class zkid_gadget : gadget<FieldT> {
       bit_packers.emplace_back(new packing_gadget<FieldT>(pb, k_bound_bits, k_bound));
 
       // pack k_bits into k_packed
+      k_bits.allocate(pb, 32);
       bit_packers.emplace_back(new packing_gadget<FieldT>(pb, k_bits, k_packed));
 
       // constrain k_packed to be less than k_bound
@@ -253,8 +257,9 @@ class zkid_gadget : gadget<FieldT> {
 
       // construct serial number hash
       pb_variable_array<FieldT> salt_bits(salt_kbound_bits.begin(), salt_kbound_bits.end()-32);
+      salt_bits.insert(salt_bits.begin(), 3, ZERO);
[…]

### 2018-05-13 test/authentication/zkMerkelTreeAuthenticatorTest.cpp

@@ -74,7 +74,7 @@ TEST(zkIDTest, TestProofGeneration){
   ProofRequest proof;
   VerificationData verification_data;
 
-  ProofRequestFromJson("test/res/credentials/test_credential_proof.json", proof);
+  ProofRequestFromJson("test/res/test_credential_proof.json", proof);
   libff::alt_bn128_pp::init_public_params();
   zkID<sha256_two_to_one_hash_gadget> authenticator(proof.path.size(), 32);
   bool verifiable = authenticator.GetVerificationData(proof, verification_data);

### 2018-05-13 src/ui/js/zkid.js
Added public inputs

@@ -3,8 +3,8 @@ issuer_abi = JSON.parse('[{"constant":false,"inputs":[],"name":"getMerkleRootAdd
 IssuerContract = web3.eth.contract(issuer_abi);
 currentBlock = null;
 
-function ProofToBytes(proof, publicInputs) {
-    return [].concat(
+function ProofToBytes(proof) {
+    proof_bytes =  [].concat(
         web3.utils.hexToBytes(proof["A"][0]),
         web3.utils.hexToBytes(proof["A"][1]),
         web3.utils.hexToBytes(proof["A_p"][0]),
@@ -22,10 +22,12 @@ function ProofToBytes(proof, publicInputs) {
         web3.utils.hexToBytes(proof["H"][0]),
         web3.utils.hexToBytes(proof["H"][1]),
         web3.utils.hexToBytes(proof["K"][0]),
-        web3.utils.hexToBytes(proof["K"][1]));
+        web3.utils.hexToBytes(proof["K"][1]),
+        proof["public_inputs"].length()); //max 255 inputs
 
-        //TODO: Append public inputs
-}
+    return proof["public_inputs"].reduce(function(acc,e){
+        acc.concat(web3.utils.hexToBytes(e));
+    },proof_bytes);
 
 
 var CredentialMethod = function (methodName, method, abi) {

### 2018-05-13 paper/paper.tex
Started some secionts on implementation

@@
 \usepackage[numbers]{natbib}
+\usepackage{listings,xcolor}
 \usepackage{todonotes}
@@
 
+\subsection{dApp Framework and Credential-Enabled Contracts}
+
+The properly interface with the ZKID Service a dApp will have to provide an annotated ABI for its dependant contract(s).
+The required annotations describe the required credentials for a given method within the smart contract and will
+be used to propery construct public inputs and subsequently generate proofs for credentials. An annotated ABI function
+would appear as follow:
+
+\begin{lstlisting}
+
+  {"constant":false,
+   "name":"Join",
+   "inputs":[],
+   "outputs":[],
+   "payable":false,
+   "type":"function","
+    "credentials":[
+      {"contract_salt":"0xdeadbeef",
+      "high_bound":150,
+      "low_bound":18,
+      "k_factor":1,
+      "description": "Confirms holder is over 18."
+      }
+    ]
+
+\end{lstlisting}
+
+Note that the description field is not nessesary for generation / verification of proofs, but is supplied soley for
+the use of the credential-acknowledgement framework described later.
+
+Additionally, all credential-enabled contracts are required to implement a GetMerkleTreeAddress function that can provide
+the caller with the IPFS address of its merkle root. This is pertinent to the generation of the nessesary Merkle Tree membership
+proofs and proof generation will be unsuccessful if ignored.
+
+\subsection{ZKID Service}
+
+\subsubsection{libsnark}
+
+\subsubsection{JSON RPC Service}
+
+The ZKID client application acts as a JSON RPC service that can handle requests from client dApps. For the simplest implementation,
+the RPC service offered a single procedure: GenerateProofs. This procedure takes as input all the fields nessesary
+to construct the required set of public inputs for the proofs. If proof generation was successful, the service will respond with a 
+set of generated proofs as well as their relative public inputs. The returned proofs can then be sent to the verifier contract.
+
+\subsection{Verifiers}
+
+It is expected, although not required, that credential-enabled contracts perform their own verification. For this reason, we have
+provided a Solidity library enables contracts to verify proofs autonomously. The verifier library follows a scheme similar to that
+of Zokrates [insert citation here]. The library exposes a single method to be utlized by the higher-level contract: verifyTx. This 
+method does precisely what the name implies and verifies as set of proofs encoded as bytes and returns true if all proofs where sucessfully
+verified and false otherwise.
+
+It is important to note that all verification calculations are done on-chain and therefore can potentially require immense amounts of gas.
+For this reason, the number of proofs requested for verification should be kept to a minimum.
+
+\subsection{Issuers}
+
+Although there is no strict template for an issuer (asside from the credential contruction), we purpose a scheme that we believe
+will offers most of the elementary functions of an issuer.
+
+\subsubsection{InterPlanetary File System (IPFS)}
+
+As designed, the ZKID service expects verifiers to store their issued-credential merkle trees using the distributed file system service, InterPlanetary File System (IPFS).
+By utilizing IPFS, the ZKID service promotes the distributed nature of its environment and further encourages issuers to take advantage of said distributed nature. All issuer
+contracts must supply a GetMerkleTreeAddress method that returns the IPFS address of their merkle root. Every issuer must also append the hashes of every issued credential 
+to their merkle tree so that verifiers and clients can construct merkle tree paths and subsequently merkle tree membership proofs as nessesary.
+
 \section{Benchmarks}
@@
 \section{Example Application}
+
+To demonstrate the facilities provided by the our system we developed a simple lottery dApp that requries participants to be
+both over the age of 18 and have American Citizenship to participate. Along with the dApp, we created a credential-acknowledgement
+framework that would allow applications to prompt users for the required credentials before any proofs are generated.
 

### 2018-05-13 paper/paper.tex
Added details about ZKID Web3 Framework

@@
 
+\subsection{Credential Scheme}
+
+\subsection{The ZKID Service}
+
+\subsubsection{libsnark}
+
+\subsubsection{JSON RPC}
+
+The ZKID client application acts as a JSON RPC service that can handle requests from client dApps. For the simplest implementation,
+the RPC service offered a single procedure: GenerateProofs. This procedure takes as input all the fields nessesary
+to construct the required set of public inputs for the proofs. If proof generation was successful, the service will respond with a 
+set of generated proofs and relevant public inputs. The returned proofs can then be sent to the verifier contract.
+
+\subsection{Verifiers}
+
+It is expected, although not required, that credential-enabled contracts perform their own proof verification. For this reason, we have
+developed a Solidity library that enables contracts to verify proofs autonomously. The verifier library follows a scheme similar to that
+of Zokrates [insert citation here]. The library exposes a single method to be utlized by the higher-level contract: verifyTx. This 
+method does precisely what the name implies and verifies as set of proofs encoded as bytes and returns true if all proofs where sucessfully
+verified and false otherwise.
+
+It is important to note that all verification calculations are done on-chain and therefore can potentially require immense amounts of gas.
+For this reason, the number of proofs requested for verification should be kept to a minimum.
+
+\subsection{Issuers}
+
+Although there is no strict template for an issuer (asside from the credential contruction), we purpose a scheme that we believe
+will offers most of the elementary functions of an issuer. This basic scheme involves 2 main functions:
+credential-holder stake and distributed merkle tree storage.
+
+\subsubsection{Credential-Holder Stake}
+
+An obvious vulenerability of the credential system as described is the ability to share credentials. So, for example, an uncredible could may
+a credible party for a specific credential. We proprose that an issuer's require a credential-requester to submit a stake when 
+applying for a credential. This stake can be redeemed by an user that can provide the issuer contract with a specified pre-image. Once 
+redeemed, the credential because invalidated. Therefore, if a dishonest party were to give away their credential, the new holder of the credential
+could steal the original holder's stake. This requires issuers to set their stakes high enough such that no party would be willing to pay the
+price of the stake for the credential. A stake system could also lead to varying "tiers" of issuers where issuers that require higher stakes could be 
+percieved as having higher credibility do the lower probability of users sharing said issuer's credential.
+
+\subsubsection{InterPlanetary File System (IPFS)}
+
+As designed, the ZKID service expects verifiers to store their issued-credential merkle trees using the distributed file system service, InterPlanetary File System (IPFS).
+By utilizing IPFS, the ZKID service promotes the distributed nature of its environment and further encourages issuers to take advantage of said distributed nature. All issuer
+contracts must supply a GetMerkleTreeAddress method that returns the IPFS address of their merkle root. Every issuer must also append the hashes of every issued credential 
+to their merkle tree so that verifiers and clients can construct merkle tree paths and subsequently merkle tree membership proofs as nessesary.
+
 \subsection{dApp Framework and Credential-Enabled Contracts}
 
+Add some Introduction here
+
+\subsubsection{Credential Annotated ABI}
 The properly interface with the ZKID Service a dApp will have to provide an annotated ABI for its dependant contract(s).
@@
 would appear as follow:
-
 \begin{lstlisting}
@@
       {"contract_salt":"0xdeadbeef",
-      "high_bound":150,
+      "high_bound":255,
       "low_bound":18,
-      "k_factor":1,
+      "k_bound":1,
       "description": "Confirms holder is over 18."
@@
     ]
-
+  }
 \end{lstlisting}
@@
 
-Additionally, all credential-enabled contracts are required to implement a GetMerkleTreeAddress function that can provide
-the caller with the IPFS address of its merkle root. This is pertinent to the generation of the nessesary Merkle Tree membership
-proofs and proof generation will be unsuccessful if ignored.
+\subsubsection{ZKID web3 Framework}
 
-\subsection{ZKID Service}
+To a dApp's migration to credentail-enabled contracts as smooth as possible we have supplied a ZKID framework that interfaces
+with our prove-generation service and seemlessly collects and supplies verifcation arguments to credential-enabled methods. This 
+allows dApp creators to integrate credential functionality without changing their already developed application code.
 
-\subsubsection{libsnark}
+To utlize the framework a dApp simply replaces all existing contract calls with calls to their credential accepting counterparts. 
+This can be accomplished very concisely by wrapping the credial-accepting method call with partially applied
+function. A full implementation of this exists in our example application and is depicted in [INSERT FIG NUMBER];
+\begin{lstlisting}
+function OnJoinClick() {
+  var credBlock = new CredentialBlock("Join", PartialAppJoin(), lottery_abi);
+    credBlock.display();
+}
 
-\subsubsection{JSON RPC Service}
+function PartialAppJoin(/* Insert non-proof arguments here*/) {
+  return function (proof_bytes) {
+    contractInstance.methods["Join"](/* Non-Proof Arguments*/ ,proof_bytes).send();
+  }
+}
 
-The ZKID client application acts as a JSON RPC service that can handle requests from client dApps. For the simplest implementation,
-the RPC service offered a single procedure: GenerateProofs. This procedure takes as input all the fields nessesary
-to construct the required set of public inputs for the proofs. If proof generation was successful, the service will respond with a 
-set of generated proofs as well as their relative public inputs. The returned proofs can then be sent to the verifier contract.
+\end{lstlisting}
 
-\subsection{Verifiers}
-
-It is expected, although not required, that credential-enabled contracts perform their own verification. For this reason, we have
-provided a Solidity library enables contracts to verify proofs autonomously. The verifier library follows a scheme similar to that
-of Zokrates [insert citation here]. The library exposes a single method to be utlized by the higher-level contract: verifyTx. This 
-method does precisely what the name implies and verifies as set of proofs encoded as bytes and returns true if all proofs where sucessfully
-verified and false otherwise.
-
-It is important to note that all verification calculations are done on-chain and therefore can potentially require immense amounts of gas.
-For this reason, the number of proofs requested for verification should be kept to a minimum.
-
-\subsection{Issuers}
-
-Although there is no strict template for an issuer (asside from the credential contruction), we purpose a scheme that we believe
-will offers most of the elementary functions of an issuer.
-
-\subsubsection{InterPlanetary File System (IPFS)}
-
-As designed, the ZKID service expects verifiers to store their issued-credential merkle trees using the distributed file system service, InterPlanetary File System (IPFS).
-By utilizing IPFS, the ZKID service promotes the distributed nature of its environment and further encourages issuers to take advantage of said distributed nature. All issuer
-contracts must supply a GetMerkleTreeAddress method that returns the IPFS address of their merkle root. Every issuer must also append the hashes of every issued credential 
-to their merkle tree so that verifiers and clients can construct merkle tree paths and subsequently merkle tree membership proofs as nessesary.
+In the above example, "Join" allowed a users to join a lottery if they have the required credentials. Originally, took a number of non-proof arguments. 
+The credential enabled join now takes the non-proof arguments as well as proof arguments.
+This partial application hides the non-proof arguments from the ZKID CredentialBlock and allows the CredentialBlock to
+supply the proof arguments post proof-generation. The dApp's code has now migrated its call to "Join" to a credential-enabled call with minimal additions.
 

### 2018-05-13 include/proving/zkidMTA.h
Get merkle root working. Dont mind the crazy printfs....

@@ -89,7 +89,6 @@ class zkID : public zkidProofGadget
         bit_vector_from_string(attributes_bv, proof_req.attributes);
         bit_vector_from_string(upper_bounds_bv, proof_req.upper_bounds);
         bit_vector_from_string(lower_bounds_bv, proof_req.lower_bounds);
-
         //Fills in the variables on the protoboard
         _zkid.generate_r1cs_witness(secret_key_bv,
                                     upper_bounds_bv,
@@ -102,7 +101,26 @@ class zkID : public zkidProofGadget
                                     root_hash_bv,
                                     address,
                                     auth_path);
-        printf("HERE4\n");
+
+        std::cout << "Tree depth: " << tree_depth << std::endl;
+
+        std::cout << "Address: " << address << std::endl;
+
+        std::cout << "Address bits: " << hex_from_bit_vector(address_bits) << std::endl;
+
+        std::cout << "Merkle Root: " << hex_from_bit_vector(_zkid.merkle_root_digest.get_digest()) << std::endl;
+
+        std::cout << "Expected root: " << hex_from_bit_vector(root_hash_bv) << std::endl;
+
+        std::cout << "Serial packed: " << HexStringFromLibsnarkBigint(_pb.val(_zkid.serial_number_packed).as_bigint()) << std::endl;
+
+        std::cout << "Serial digest: " << hex_from_bit_vector(_zkid.serial_number_digest.get_digest()) << std::endl;
+
+        std::cout << "Leaf inputs: " << hex_from_bit_vector(_zkid.leaf_inputs->get_block()) << std::endl;
+        std::cout << "Leaf len: " << _zkid.leaf_inputs->get_block().size() << std::endl;
+
+        std::cout << "Serial inputs: " << hex_from_bit_vector(_zkid.serial_inputs->get_block()) << std::endl;
+
         //Generate a authentication proof if the pb is satisified.
         if (!_pb.is_satisfied())
             return false;

### 2018-05-13 include/proving/zkidMTACircuit.h

@@ -47,7 +47,7 @@ public:
         lower->generate_r1cs_constraints();
     }
     void generate_r1cs_witness(){
-        upper->generate_r1cs_witnwss();
+        upper->generate_r1cs_witness();
         lower->generate_r1cs_witness();
     }
 };
@@ -263,6 +263,7 @@ class zkid_gadget : gadget<FieldT> {
 
       // pack serial_number low bits
       pb_variable_array<FieldT> serial_low_bits(serial_number_digest.bits.end()-FieldT::capacity(), serial_number_digest.bits.end());
+      std::cout << "SLB size: "<< serial_low_bits.size() << std::endl;
       bit_packers.emplace_back(new packing_gadget<FieldT>(pb, serial_low_bits,  serial_number_packed));
 
       // pack merkle_root
@@ -271,9 +272,9 @@ class zkid_gadget : gadget<FieldT> {
 
       // construct merkle root
       pb_variable_array<FieldT> attribute_bits;
-      attribute_bits.allocate(pb, digest_len);
+      attribute_bits.allocate(pb, 7*attribute_size);;
       attr_splitter.reset(new multipacking_gadget<FieldT>(pb, attribute_bits, attributes_split, attribute_size));
-      leaf_inputs.reset(new block_variable<FieldT>(pb,  std::vector<pb_variable_array<FieldT>>({private_key, attribute_bits}), "leaf inputs"));
+      leaf_inputs.reset(new block_variable<FieldT>(pb,  std::vector<pb_variable_array<FieldT>>({private_key, pb_variable_array<FieldT>(attribute_size, ZERO), attribute_bits}), "leaf inputs"));
       leaf_hasher.reset(new HashT(pb, 512, *leaf_inputs, leaf_digest, "leaf hasher"));
 
       address_bits.allocate(pb, tree_depth);
@@ -294,6 +295,9 @@ class zkid_gadget : gadget<FieldT> {
 
     for(auto& range : range_proofs)
       range->generate_r1cs_constraints();
+
+    for(auto& packer : bit_packers)
+      packer->generate_r1cs_constraints(true);
 
     k_compare->generate_r1cs_constraints();
 
@@ -343,20 +347,27 @@ class zkid_gadget : gadget<FieldT> {
     private_key.fill_with_bits(this->pb, secret_key);
 
     merkle_root_digest.generate_r1cs_witness(merkle_root);
[…]

### 2018-05-13 test/authentication/zkMerkelTreeAuthenticatorTest.cpp

@@ -4,7 +4,7 @@
 #include "proving/zkidMTA.h"
 #include "util/zkid_helpers.h"
 
-
+/*
 #define M_TREE_LENGTH 3
 
 TEST(zkMTATest, TestProofGenerationPbSatisfaction){
@@ -68,7 +68,7 @@ TEST(zkMTATest, TestVerifyFail){
 
   ASSERT_FALSE(verified);
 }
-
+*/
 
 TEST(zkIDTest, TestProofGeneration){
   ProofRequest proof;

### 2018-05-13 test/generate_credential.py

@@ -2,6 +2,7 @@
 import struct
 import json
 from os import urandom
+from sys import argv
 from random import getrandbits, randint
 from hashing.sha_compress import path, sha_compress
 
@@ -13,10 +14,10 @@ class Credential(object):
         self.secret_key = secret_key
         self.attributes = attributes
 
-        self.attr_string = b"\x00"*4+struct.pack(">"+"I"*7, *attributes)
+        self.attr_string = struct.pack(">"+"I"*7, *attributes)
 
-    def generate_proof_params(self, contract_salt, upper_bounds, lower_bounds, k_bound, k):
-        serial = sha_compress(b"\x00"+self.secret_key+ b"\x00"+contract_salt + struct.pack(">I", k))
+    def generate_proof_params(self, contract_salt, upper_bounds, lower_bounds, k_bound, k, n):
+        serial = sha_compress(self.secret_key+ b"\x00"+contract_salt + struct.pack(">I", k))
         return {"sk" : self.secret_key.hex(),
                  "attributes" : self.attr_string.hex(),
                  "upper_bounds": struct.pack(">"+"I"*7, *upper_bounds).hex(),
@@ -25,10 +26,10 @@ class Credential(object):
                  "k": k,
                  "contract_salt": contract_salt.hex(),
                  "serial_number": serial.hex(),
-                 "merkle_proof" : path(8, b"\x00"+self.secret_key+self.attr_string)}
+                 "merkle_proof" : path(n, self.secret_key+b"\x00"*4+self.attr_string)}
 
 if __name__ == "__main__":
-    sk = urandom(31)
+    sk = urandom(32)
     attrs = [getrandbits(32) for _ in range(7)]
     cred = Credential(sk, attrs)
     uppers = list(map(lambda x: randint(x, 2**32), attrs))
@@ -36,5 +37,6 @@ if __name__ == "__main__":
     k = randint(0, 2**32)
     k_bound = randint(k, 2**32)
     contract_salt = urandom(27)
-    proof = cred.generate_proof_params(contract_salt, uppers, lowers, k_bound, k)
+    n = int(argv[1])
+    proof = cred.generate_proof_params(contract_salt, uppers, lowers, k_bound, k, n)
     pretty_print(proof)

### 2018-05-13 test/authentication/zkMerkelTreeAuthenticatorTest.cpp
Add tests and exclude IPFS tests from travis

@@ -5,7 +5,7 @@
 #include "util/zkid_helpers.h"
 
 
-#define M_TREE_LENGTH 3
+#define M_TREE_LENGTH 32
 
 TEST(zkMTATest, TestProofGenerationPbSatisfaction){
     std::string root;
@@ -80,3 +80,50 @@ TEST(zkIDTest, TestProofGeneration){
   bool verifiable = authenticator.GetVerificationData(proof, verification_data);
   ASSERT_TRUE(verifiable);
 }
+
+TEST(zkIDTest, TestVerify){
+  ProofRequest proof;
+  VerificationData verification_data;
+
+  ProofRequestFromJson("test/res/test_credential_proof.json", proof);
+  libff::alt_bn128_pp::init_public_params();
+  zkID<sha256_two_to_one_hash_gadget> authenticator(proof.path.size(), 32);
+
+  LibsnarkVerificationData libsnark_data;
+  authenticator.GetVerificationData(proof, verification_data, &libsnark_data);
+  const bool verified = r1cs_ppzksnark_verifier_strong_IC<libff::alt_bn128_pp>(authenticator.GetVerificationKey(),
+                                                         libsnark_data.primary_input,
+                                                         libsnark_data.proof);
+
+  ExportProof(libsnark_data, "test/res/proof.export");
+
+  ASSERT_TRUE(verified);
+}
+
+
+TEST(zkIDTest, TestExportVerifier){
+  zkID<sha256_two_to_one_hash_gadget> zkid(M_TREE_LENGTH, 32);
+
+  auto vk_pp = zkid.GetVerificationKey();
+  VerificationKey vk = ExtractVerificationKey(vk_pp);
+
+  ExportVerificationKey(vk, "test/res/verification.sol.tmpl", "test/res/verification.sol");
+}
+
+TEST(zkIDTest, TestVerifyFail){
+  ProofRequest proof;
+  VerificationData verification_data;
+
+  ProofRequestFromJson("test/res/test_credential_proof_fail.json", proof);
+  libff::alt_bn128_pp::init_public_params();
+  zkID<sha256_two_to_one_hash_gadget> authenticator(proof.path.size(), 32);
+
+  LibsnarkVerificationData libsnark_data;
+  authenticator.GetVerificationData(proof, verification_data, &libsnark_data);
+  const bool verified = r1cs_ppzksnark_verifier_strong_IC<libff::alt_bn128_pp>(authenticator.GetVerificationKey(),
+                                                                               libsnark_data.primary_input,
[…]

### 2018-05-13 include/proving/zkidMTACircuit.h
Remove unnecessary includes

@@ -6,10 +6,6 @@
 #include <libsnark/gadgetlib1/gadgets/merkle_tree/merkle_tree_check_read_gadget.hpp>
 #include <libsnark/gadgetlib1/gadgets/basic_gadgets.hpp>
 
-//TODO remove:
-#include "util/libsnark_helpers.h"
-
-
 using namespace libsnark;
 
 
@@ -118,8 +114,6 @@ public:
         leaf_digest->generate_r1cs_witness(leaf);
         path_var->generate_r1cs_witness(address, auth_path);
         merkle_check->generate_r1cs_witness();
-        printf("Merkle root:\n");
-        std::cout << hex_from_bit_vector(merkle_check->root.get_digest()) << std::endl;
 
         root_digest->generate_r1cs_witness(root);
         unpacker->generate_r1cs_witness_from_packed();
@@ -239,7 +233,7 @@ class zkid_gadget : gadget<FieldT> {
       // constrain each attribute to be in-bounds
       for(int i = 0; i < num_attributes; ++i)
         range_proofs.emplace_back(new zkrange_gadget<FieldT>(pb, attribute_size, upper_bounds_split[i], lower_bounds_split[i], attributes_split[i]));
-      
+
       // pack salt_bits into salt
       salt_kbound_bits.allocate(pb, digest_len - 8);
       bit_packers.emplace_back(new packing_gadget<FieldT>(pb, pb_variable_array<FieldT>(salt_kbound_bits.begin(), salt_kbound_bits.end()-32), salt_kbound_packed));

### 2018-05-13 src/ui/js/zkid.js
Removed client-provided public inputs

@@ -4,7 +4,7 @@ IssuerContract = web3.eth.contract(issuer_abi);
 currentBlock = null;
 
 function ProofToBytes(proof) {
-    proof_bytes =  [].concat(
+    return [].concat(
         web3.utils.hexToBytes(proof["A"][0]),
         web3.utils.hexToBytes(proof["A"][1]),
         web3.utils.hexToBytes(proof["A_p"][0]),
@@ -22,21 +22,9 @@ function ProofToBytes(proof) {
         web3.utils.hexToBytes(proof["H"][0]),
         web3.utils.hexToBytes(proof["H"][1]),
         web3.utils.hexToBytes(proof["K"][0]),
-        web3.utils.hexToBytes(proof["K"][1]),
-        proof["public_inputs"].length()); //max 255 inputs
-
-    return proof["public_inputs"].reduce(function(acc,e){
-        acc.concat(web3.utils.hexToBytes(e));
-    },proof_bytes);
-
-
-var CredentialMethod = function (methodName, method, abi) {
-    this.methodName = methodName;
-    this.method = method;
-    this.requiredCredentials = abi.find(function (e) {
-        return e["name"] === methodName;
-    })["credentials"];
+        web3.utils.hexToBytes(proof["K"][1]));
 }
+
 
 CredentialBlock.prototype.FetchCredentialProofs = function () {
     var client = new zkidclient("http://localhost:8383");
@@ -116,6 +104,14 @@ CredentialBlock.prototype.display = function () {
 function CredentialBlock(methodName, method, abi) {
     this.action = new CredentialMethod(methodName, method, abi);
     currentBlock = this;
+}
+
+var CredentialMethod = function (methodName, method, abi) {
+    this.methodName = methodName;
+    this.method = method;
+    this.requiredCredentials = abi.find(function (e) {
+        return e["name"] === methodName;
+    })["credentials"];
 }
 
 function PostVericiationError(code, msg) {

### 2018-05-13 include/proving/zkidMTA.h
Fix test case generation

@@ -102,8 +102,6 @@ class zkID : public zkidProofGadget
                                     address,
                                     auth_path);
 
-        pb_variable_array<FieldT> k_bound_bits(_zkid.salt_kbound_bits.end() - 32, _zkid.salt_kbound_bits.end());
-
         //Generate a authentication proof if the pb is satisified.
         if (!_pb.is_satisfied())
             return false;

### 2018-05-13 include/proving/zkidMTACircuit.h

@@ -170,9 +170,9 @@ class zkid_gadget : gadget<FieldT> {
   pb_variable_array<FieldT> k_bits;
   pb_variable_array<FieldT> private_key;
 
-  digest_variable<FieldT> leaf_digest;
-  digest_variable<FieldT> merkle_root_digest;
-  digest_variable<FieldT> serial_number_digest;
+  std::shared_ptr<digest_variable<FieldT>> leaf_digest;
+  std::shared_ptr<digest_variable<FieldT>> merkle_root_digest;
+  std::shared_ptr<digest_variable<FieldT>> serial_number_digest;
 
   pb_variable_array<FieldT> address_bits;
 
@@ -194,10 +194,7 @@ class zkid_gadget : gadget<FieldT> {
 
 
  zkid_gadget(protoboard<FieldT> &pb, size_t tree_depth, size_t attribute_size) :
-  gadget<FieldT>(pb),
-    leaf_digest(pb, HashT::get_digest_len(), "leaf"),
-    merkle_root_digest(pb, HashT::get_digest_len(), "root"),
-    serial_number_digest(pb, HashT::get_digest_len(), "serial")
+  gadget<FieldT>(pb)
    {
       size_t digest_len = HashT::get_digest_len();
       // Note that all hash digests are constrained only up to the size of 1 field element
@@ -214,6 +211,10 @@ class zkid_gadget : gadget<FieldT> {
       pb.set_input_sizes(5);
       ZERO.allocate(pb);
       private_key.allocate(pb, digest_len);
+
+      leaf_digest.reset(new digest_variable<FieldT>(pb, HashT::get_digest_len(), "leaf"));
+      merkle_root_digest.reset(new digest_variable<FieldT>(pb, HashT::get_digest_len(), "root"));
+      serial_number_digest.reset(new digest_variable<FieldT>(pb, HashT::get_digest_len(), "serial"));
 
       // pack as many attributes as fit into a single field element
       size_t num_attributes = FieldT::capacity()/attribute_size;
@@ -257,14 +258,14 @@ class zkid_gadget : gadget<FieldT> {
       pb_variable_array<FieldT> salt_bits(salt_kbound_bits.begin(), salt_kbound_bits.end()-32);
       assert(salt_bits.size() == 27*8);
[…]

### 2018-05-13 include/proving/zkidProofGadget.h

@@ -11,7 +11,7 @@ class zkidProofGadget
     typedef libff::alt_bn128_pp ppt;
     typedef libff::Fr<ppt> FieldT;
     zkidProofGadget() : _pb() {}
-    virtual void GenerateProof(protoboard<FieldT> &pb, 
+    virtual void GenerateProof(protoboard<FieldT> &pb,
         VerificationData &v_data, LibsnarkVerificationData *libsnark_data = nullptr)
     {
         r1cs_ppzksnark_proof<ppt> proof = r1cs_ppzksnark_prover<ppt>(_keypair->pk, _pb.primary_input(), _pb.auxiliary_input());

### 2018-05-13 test/authentication/zkMerkelTreeAuthenticatorTest.cpp

@@ -5,7 +5,7 @@
 #include "util/zkid_helpers.h"
 
 
-#define M_TREE_LENGTH 32
+#define M_TREE_LENGTH 8
 
 TEST(zkMTATest, TestProofGenerationPbSatisfaction){
     std::string root;

### 2018-05-13 test/hashing/sha_compress.py

@@ -47,7 +47,7 @@ def path(count, leaf=None):
         sibling = urandom(32)
         right = bool(urandom(1)[0]%2)
         h = sha_compress(h+sibling if right else sibling+h)
-        tree["path"].append({"hash": sibling.hex(), "right": right})
+        tree["path"].insert(0, ({"hash": sibling.hex(), "right": right}))
     tree["root"] = h.hex()
     return tree
 

### 2018-05-13 paper/paper.tex
Stuff

@@
 \subsection{Prior Work}
-A generalized scheme was proposed by \citet{garmanDecentralizedAnonymousCredentials2013}
+Identity systems for public blockchains have been proposed before in the form of
+serivces like Civic and Uport, wherein users can acquire attestations from
+trusted issuers about facets of their identity (name, age, country of origin,
+etc). These services promise ``anonymous'' attestation, but are
+\textit{linkable}, i.e.\ multiple attestations by the same user are trivially
+identifiable, and \textit{pseudonymous}, i.e.\ attestations are
+linked to a pseudonym that is known by the credential issuer. If a credential
+issuer leaks their records, then all past activity by a user is deanonymized.
+
+A zero-knowledge credential scheme for blockchains was proposed by
+\citet{garmanDecentralizedAnonymousCredentials2013}, using zkSNARKS. Our system
+adapts this scheme for the Ethereum\cite{woodEthereumSecureDecentralised2014} blockchain and implements more expressive
+forms of credentials that can be easily utilized for ad-hoc attestations in zero-knowledge.
+
+\subsection{Protocol Overview}
+\subsubsection{Actors}
+The major actors in this protocol are \textit{issuers}, \textit{verifiers} and
+\textit{users}. A verifier is a  smart-contract that wants to ensure that
+users calling a function are authorized to do so. In order to authorize users,
+the contract designates an issuer, who is responsible for granting credentials
+to users and keeping a Merkle tree of valid credentials. The verifier then
+requires that each user provide a zero-knowledge proof that the user possesses a
+credential in the merkle tree with attributes in the required range. Both
+credential issuance and usage is done in zero-knowledge and attestations are
+reusable and unlinkable.
+
+\subsection{Implementation}
+We implement zero-knowledge proofs using the elliptic curve pairing precompiled
+contracts in Ethereum, using the Pinnochio protocol
+\cite{parnoPinocchioNearlyPractical2013}. We constructed the arithmetic circuits
+for the proofs using libsnark \cite{ben-sassonSNARKsVerifyingProgram2013}.
+Commitment trees are stored using IPFS \cite{benetIPFSContentAddressed2014}.
 
 \section{Properties and Features}
+Our zero-knowledge identity system allows for highly flexible ad-hoc issuance of
+credentials through \textit{k-show} credentials and range-bounded attributes.
+
+The public inputs are
+\begin{equation*}
+  \texttt{m\_root},\ \{l_1, \dots, l_7\},\ \{u_1, \dots, u_7\}, S, k
+\end{equation*}
+
+Each proof is an assertion that the prover holds a credential
+\begin{equation*}
+c = (sk, \{attr_1, \dots, attr_7\})  
+\end{equation*}
+ such that
+
+\begin{enumerate}[1.]
+\item The credential is a leaf of a merkle tree with root \texttt{m\_root}.
+\item The credential contains some attributes $\{attr_1, \dots, attr_7\}$ with
+  $attr_i \in [l_i,u_i]$
+\item The credential has been used fewer than $k$ times with the salt $S$
+\end{enumerate}
 
@@
 
+\subsection{Credentials}
+Each credential is of the form
+\begin{equation*}
+c =  ( \texttt{sk}, \{attr_1, \dots, attr_n\})
+\end{equation*}
+
+where $\texttt{sk} \in \{0, 1\}^\lambda$ and $attr_i \in \Z_{2^{32}}$.
+
+\subsection{Credential Requests}
+A credential request is a tuple of the form
+\begin{equation*}
+  r = (\texttt{merkle\_root}, \texttt{serial}, \{u_1, \dots,u_n\}, \{\ell_1,\dots,\ell_n\}, S, k)
+\end{equation*}
+
+where $\texttt{merkle\_root}$ is the root of a Merkle-tree of valid credential
+commitments, $u_i, \ell_i \in \Z_{2^{32}}$ are bounds on acceptable attribute
+values, $S$ is a request-specific salt, and $k\in \N$ is the allowed number of
+uses of a single credential per salt $S$.
+
+\subsection{k-show Credentials}
+Every proof $\pi$ that a user generates has as public input
+$\texttt{serial}_\pi$ which is defined as
+\begin{equation*}
+  H(\texttt{sk}_u || S_v || k)
+\end{equation*}
+
+and a public input $\texttt{k\_bound}$ such that $k\leq \texttt{k\_bound}$. For
+each proof that the verifier accepts, the verifier adds $\texttt{serial}_\pi$ to
+its nullifier set $N$. A verifier accepts $\pi$ only if $\pi \notin N$. Thus,
+for a given salt $S_v$ the user may produce up to $\texttt{k\_bound}$ distinct
+valid proofs, while remaining unlinkable. The verifier $v$ may select $S$ such
+that it changes over time, for instance such that it contains the hash of the
+most recent block with height a multiple of 1 million, which allows for
+rate-limited credentials.
+
+\subsection{Bounded-attributes}
+A proof for a given credential request $r$ must assert that $attr_i \in [\ell_i,
+u_i]$ for all $1\leq i\leq n$. This allows attestations such as ``I possess over
+\$1 million'', ``I am between the ages of 21 and 45'', or ``I live in the USA'',
+without revealing any additional information.
+
 \subsection{Credential Scheme}
+verifier
 

### 2018-05-13 include/credentials/CredentialsManager.h
Merged with Prover

@@ -5,38 +5,19 @@
 #include <string>
 #include "configuration/ConfigCredentialsInterface.h"
 #include "util/json_helpers.h"
+#include "proving/zkidVerificationStructs.h"
 
-struct Credential{
-    Credential(){};
-    Credential(std::string a, std::string l, std::string u, int kb, int _k, std::string cs, 
-        std::string sn,uint ma) : attributes(a), 
-                                          lower_bound(l),
-                                          upper_bound(u),
-                                          k(_k),
-                                          k_bound(kb),
-                                          contract_salt(cs),
-                                          serial_number(sn),
-                                          merkle_address(ma){};
-    std::string contract_salt;
-    std::string lower_bound;
-    std::string upper_bound;
-    int k_bound;
-    std::string serial_number;
-    std::string attributes;
-    int k;
-    uint merkle_address;
-};
+class CredentialsManager
+{
+  public:
+    CredentialsManager(ConfigCredentialsInterface *cred_config) : _cred_config(cred_config) {}
+    void LoadCredentials();
+    bool HasCredential(const std::string &issuer_address);
+    Credential GetCredential(const std::string &issuer_address);
 
-class CredentialsManager{
-    public:
-        CredentialsManager(ConfigCredentialsInterface* cred_config) : _cred_config(cred_config){}
-        void LoadCredentials();
-        bool HasCredential(const std::string& issuer_address);
-        Credential GetCredential(const std::string& issuer_address);
-
-    private:
-        ConfigCredentialsInterface* _cred_config;
-        std::unordered_map<std::string,Credential> _credentials; //this may be redundant since the issuer address is in the token.
+  private:
+    ConfigCredentialsInterface *_cred_config;
+    std::unordered_map<std::string, Credential> _credentials; //this may be redundant since the issuer address is in the token.
 };
 
 #endif

### 2018-05-13 include/network/zkidIPFSGateway.h

@@ -11,7 +11,7 @@ class zkidIPFSGateway : public zkidMTProvider
   public:
     zkidIPFSGateway(ConfigIPFSInterface* ipfs_config);
     void Connect(pid_t pid = 0);
-    void GetMerklePath(const std::string &merkle_address, size_t address, std::vector<std::string> &path);
+    std::string GetMerklePath(const std::string &merkle_address, size_t address, std::vector<std::string> &path);
     std::string PutMerkleTree(const std::vector<std::string>& hashes, int i = 0);
   private:
     ipfs::Client _client;

### 2018-05-13 include/proving/zkidMTA.h

@@ -1,252 +1,0 @@
-#ifndef _zkMTA_h
-#define _zkMTA_h
-
-#include <fstream>
-#include <libff/algebra/curves/public_params.hpp>
-#include <libff/algebra/curves/alt_bn128/alt_bn128_pp.hpp>
-#include <libff/algebra/fields/field_utils.hpp>
-#include <libsnark/gadgetlib1/gadget.hpp>
-#include <libsnark/gadgetlib1/gadgets/merkle_tree/merkle_tree_check_read_gadget.hpp>
-#include <libsnark/gadgetlib1/gadgets/basic_gadgets.hpp>
-#include <libsnark/zk_proof_systems/ppzksnark/r1cs_ppzksnark/r1cs_ppzksnark.hpp>
-#include <libff/common/default_types/ec_pp.hpp>
-#include <libsnark/common/default_types/r1cs_gg_ppzksnark_pp.hpp>
-#include "proving/zkidVerificationStructs.h"
-#include "proving/zkidMTACircuit.h"
-#include "util/libsnark_helpers.h"
-#include "util/zkid_helpers.h"
-#include "proving/zkidProofGadget.h"
-#include "util/json_helpers.h"
-
-using namespace libsnark;
-
-/**
- * zkMTA objects provide verification data for merkle tree authentication proofs on
- * merkle trees of depth [tree_depth].
-*/
-
-struct MTAuthenticationNode
-{
-    bool is_right;
-    std::string hash;
-    MTAuthenticationNode(const std::string &_hash, bool _is_right) : hash(_hash), is_right(_is_right){};
-    MTAuthenticationNode(){};
-};
-
-struct ProofRequest {
-  std::string secret_key;
-  std::string merkle_root;
-  std::vector<MTAuthenticationNode> path;
-
-  std::string attributes;
-  std::string upper_bounds;
-  std::string lower_bounds;
-  unsigned long k_bound;
-  unsigned long k;
-  std::string salt;
-};
-
-void ProofRequestFromJson(const std::string &path, ProofRequest &proof);
-
-template <template <typename> typename Hash>
-class zkID : public zkidProofGadget
-{
-  public:
- zkID(int tree_depth, int attribute_size) : _zkid(_pb, tree_depth, attribute_size), attribute_size(attribute_size)
-    {
-      _zkid.generate_r1cs_constraints();
-      auto cs = _pb.get_constraint_system();
[…]

### 2018-05-13 include/proving/zkidProver.h

@@ -1,15 +1,26 @@
 #ifndef _zkidProver_h
 #define _zkidProver_h
 
-#include "configuration/ConfigProverInterface.h"
 #include "zkidVerificationStructs.h"
+#include "util/zkid_helpers.h"
+
+struct ProofRequest {
+  std::string secret_key;
+  std::string merkle_root;
+  std::vector<std::string> path;
+  size_t address;
+  std::string attributes;
+  std::string upper_bounds;
+  std::string lower_bounds;
+  unsigned long k_bound;
+  unsigned long k;
+  std::string salt;
+};
+
 
 class zkidProver{
     public:
-        zkidProver(ConfigProverInterface* prover_config) : _prover_config(prover_config){};
-        bool GenerateProof(const Credential& c,const CredentialRequest& req, const std::vector<std::string>& merkle_path, CredentialProof& proof){return false; /* Actually generate a proof */};
-    private:
-        void RetrieveMerkleTree(const std::string& issuer_address);
-        ConfigProverInterface* _prover_config = nullptr;
+         virtual bool GetCredentialProof(ProofRequest &proof_req, CredentialProof &data,
+                             LibsnarkCredentialProof *libsnark_data = nullptr) = 0;
 };
 #endif

### 2018-05-13 include/proving/zkidVerificationStructs.h

@@ -5,18 +5,38 @@
 #include <vector>
 #include <string>
 
-
 enum VerificationErrorCode
 {
     //TODO: Define some error codes.
 };
 
-struct CredentialRequest{
-  std::string contract_salt;
-  std::string merkle_root_address;
-  std::string lower_bound;
-  std::string upper_bound;
-  int k_bound;
+struct Credential
+{
+    Credential(){};
+    Credential(std::string a, std::string key, int _k, std::string cs, size_t ma) : attributes(a),
+                                                                         k(_k),
+                                                                         contract_salt(cs),
+                                                                         secret_key(key),
+                                                                         merkle_address(ma){};
+    std::string secret_key;
+    std::string contract_salt;
+    std::string attributes;
+    int k;
+    size_t merkle_address;
+};
+
+struct AttributeRequest
+{
+    std::string lower_bound;
+    std::string upper_bound;
+};
+
+struct CredentialRequest
+{
+    std::string contract_salt;
+    std::string merkle_root_address;
+    std::vector<AttributeRequest> attribute_requests;
+    int k_bound;
 };
 
 struct CredentialProof
@@ -33,20 +53,15 @@ struct CredentialProof
 
 struct VerificationKey
 {
-    std::array<std::string,4> A;
-    std::array<std::string,2> B;
-    std::array<std::string,4> C;
-    std::array<std::string,4> gamma;
-    std::array<std::string,2> gammaBeta1;
-    std::array<std::string,4> gammaBeta2;
-    std::array<std::string,4> Z;
-    std::array<std::string,2> IC0;
-    std::vector<std::array<std::string,2>> ICs;
-};
-
-struct VerificationData
-{
-    CredentialProof proof;
+    std::array<std::string, 4> A;
+    std::array<std::string, 2> B;
+    std::array<std::string, 4> C;
+    std::array<std::string, 4> gamma;
+    std::array<std::string, 2> gammaBeta1;
+    std::array<std::string, 4> gammaBeta2;
+    std::array<std::string, 4> Z;
+    std::array<std::string, 2> IC0;
+    std::vector<std::array<std::string, 2>> ICs;
 };
 
 struct VerificationError

### 2018-05-13 src/credentials/CredentialsManager.cpp

@@ -16,11 +16,8 @@ void CredentialsManager::LoadCredentials(){
     for(int i = 0; i < creds_json.size(); i++){
         Json::Value current_cred = creds_json[i];
         _credentials[current_cred["contract_salt"].asString()] = Credential(current_cred["attributes"].asString(), 
-                                                                            current_cred["lower_bound"].asString(),
-                                                                            current_cred["upper_bound"].asString(),
-                                                                            current_cred["k_bound"].asInt(),
+                                                                            current_cred["secret_key"].asString(),
                                                                             current_cred["k"].asInt(),
                                                                             current_cred["contract_salt"].asString(),
-                                                                            current_cred["serial_number"].asString(),
                                                                             current_cred["merkel_address"].asInt());}
 }

### 2018-05-13 src/network/IPFSServiceController.cpp

@@ -16,8 +16,6 @@ void IPFSServiceController::StartService(char** argv)
     {
         this->_ipfs_process_id = pid;
     }
-
-    free(argv);
 }
 
 void IPFSServiceController::StopService()

### 2018-05-13 src/network/ZkidRPCServer.cpp

@@ -39,9 +39,14 @@ CredentialRequest ZkidRPCServer::CredentialRequestFromJson(const Json::Value &cr
     CredentialRequest cred_desc;
     cred_desc.contract_salt = cred_json["contract_salt"].asString();
     cred_desc.merkle_root_address = cred_json["merkle_root_address"].asString();
-    cred_desc.lower_bound = cred_json["lower_bound"].asString();
-    cred_desc.upper_bound = cred_json["upper_bound"].asString();
     cred_desc.k_bound = cred_json["k_bound"].asInt();
+
+    for(const Json::Value& attr_req_json : cred_json["requested_attributes"]){
+        AttributeRequest attr_request;
+        attr_request.lower_bound = attr_req_json["lower_bound"].asString();
+        attr_request.upper_bound = attr_req_json["upper_bound"].asString();
+        cred_desc.attribute_requests.push_back(attr_request);
+    }
 
     return cred_desc;
 }

### 2018-05-13 src/network/ZkidService.cpp

@@ -1,9 +1,9 @@
 #include "network/ZkidService.h"
+#include <libsnark/gadgetlib1/gadgets/hashes/sha256/sha256_gadget.hpp>
 
 std::shared_ptr<spdlog::logger> ZkidService::console = spdlog::stderr_color_mt("zkid");
 
-ZkidService::ZkidService(ConfigZkidServiceInterface *service_config, CredentialsManager *cred_manager, zkidMTProvider* mt_provider) : 
-    _service_config(service_config), _cred_manager(cred_manager), _http_server(service_config->GetServicePort()), _mt_provider(mt_provider)
+ZkidService::ZkidService(ConfigZkidServiceInterface *service_config, CredentialsManager *cred_manager, zkidMTProvider *mt_provider) : _service_config(service_config), _cred_manager(cred_manager), _http_server(service_config->GetServicePort()), _mt_provider(mt_provider)
 
 {
     _rpc_server = std::make_shared<ZkidRPCServer>(_http_server, _service_config);
@@ -26,13 +26,24 @@ void ZkidService::Stop()
 
 bool ZkidService::GetProofForCredential(const CredentialRequest &cred, CredentialProof &proof)
 {
+    std::string attribute_string;
+
+    for (int i = 0; i < cred.attribute_requests.size(); i++)
+    {
+        auto cur_attribute = cred.attribute_requests[i];
+        attribute_string +=
+            "attribute_index: " + std::to_string(i) + "\n" +
+            "lower_bound: " + cur_attribute.lower_bound + "\n" +
+            "upper_bound: " + cur_attribute.upper_bound + "\n";
+    }
+
     console->info("Recieved request for proof of credential: \n \
-        issuer_address: {0} \n \
-        merkle_root_address: {1} \n \
-        lower_bound: {2} \n \
-        upper_bound: {3} \n \
-        k_bound: {4}",
-                  cred.contract_salt, cred.merkle_root_address, cred.lower_bound, cred.upper_bound, cred.k_bound);
+        contract_salt: {0} \n \
+        merkle_root_address: {1} \n \ 
+        k_bound: {2} \n \
+        With Attributes: \n \
+        {3}",
+                  cred.contract_salt, cred.merkle_root_address, cred.k_bound, attribute_string);
 
     return GenerateProofForCredential(cred, proof);
 }
@@ -44,23 +55,49 @@ int ZkidService::GetPort()
 
 bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_request, CredentialProof &proof)
 {
[…]

### 2018-05-13 src/ui/js/site.js

@@ -1,5 +1,5 @@
 web3 = new Web3(new Web3.providers.HttpProvider("http://localhost:8545"));
-lottery_abi = JSON.parse('[{"constant":false,"inputs":[{"indexed": false,"name": "proofs","type": "uint[]"}],"name":"Join","outputs":[],"payable":false,"type":"function","credentials":[{"contract_salt":"0xdeadbeef","upper_bound":0,"lower_bound":0,"k_bound":0,"description":"Confirms holder is over 18."},{"contract_salt":"0xbeefdead","upper_bound":100,"lower_bound":18,"k_bound":1,"description":"Confirms holder is American."}]}]')
+lottery_abi = JSON.parse('[ { "constant": false, "inputs": [ { "indexed": false, "name": "proofs", "type": "uint[]" } ], "name": "Join", "outputs": [], "payable": false, "type": "function", "credentials": [ { "contract_salt": "0xdeadbeef", "requested_attributes": [ { "attribute_idx": 0, "upper_bound": 0, "lower_bound": 0, "k_bound": 0, "description": "Confirms holder is over 18." }, { "attribute_idx": 1, "upper_bound": 100, "lower_bound": 18, "k_bound": 1, "description": "Confirms holder is American." } ] } ] } ]');
 
 LotteryContract = web3.eth.contract(lottery_abi);
 contractInstance = LotteryContract.at("CONTRACT_ADDR");

### 2018-05-13 test/authentication/zkMerkelTreeAuthenticatorTest.cpp

@@ -1,96 +1,33 @@
 #include <gtest/gtest.h>
 #include <libsnark/gadgetlib1/gadgets/hashes/sha256/sha256_gadget.hpp>
 #include <libff/algebra/curves/alt_bn128/alt_bn128_pp.hpp>
-#include "proving/zkidMTA.h"
+#include "proving/zkidProverImpl.h"
 #include "util/zkid_helpers.h"
 
 
 #define M_TREE_LENGTH 32
 
-TEST(zkMTATest, TestProofGenerationPbSatisfaction){
-    std::string root;
-    std::string leaf;
-    std::vector<MTAuthenticationNode> path;
-    VerificationData verification_data;
-
-    AuthenticationArgsFromJson("test/res/merkle_path_test_pass.json",leaf,root,path);
-    printf("Path len: %d\n", path.size());
-    libff::alt_bn128_pp::init_public_params();
-    zkMTA<sha256_two_to_one_hash_gadget> authenticator(path.size());
-    bool verifiable = authenticator.GetVerificationData(leaf,root,path,verification_data);
-    ASSERT_TRUE(verifiable);
-}
-
-TEST(zkMTATest, TestVerify){
-    std::string root;
-    std::string leaf;
-    std::vector<MTAuthenticationNode> path;
-    VerificationData verification_data;
-
-    AuthenticationArgsFromJson("test/res/merkle_path_test_pass.json",leaf,root,path);
-    zkMTA<sha256_two_to_one_hash_gadget> authenticator(path.size());
-    LibsnarkVerificationData libsnark_data;
-    authenticator.GetVerificationData(leaf,root,path,verification_data,&libsnark_data);
-
-    const bool verified = r1cs_ppzksnark_verifier_strong_IC<libff::alt_bn128_pp>(authenticator.GetVerificationKey(),
-      libsnark_data.primary_input,libsnark_data.proof);
-
-    ExportProof(libsnark_data, "test/res/proof.export");
-
-    ASSERT_TRUE(verified);
-}
-
-TEST(zkMTATest, TestExportVerifier){
-  zkMTA<sha256_two_to_one_hash_gadget> zkidMTA(M_TREE_LENGTH);
-
-  auto vk_pp = zkidMTA.GetVerificationKey();
-  VerificationKey vk = ExtractVerificationKey(vk_pp);
-
-  ExportVerificationKey(vk, "test/res/verification.sol.tmpl", "test/res/verification.sol");
-}
-
[…]

### 2018-05-13 util/zkid_helpers.cpp

@@ -1,9 +1,7 @@
 #include "zkid_helpers.h"
 
-CredentialProof ExtractCredentialProof(libsnark::r1cs_ppzksnark_proof<libff::alt_bn128_pp> &proof)
+void ExtractCredentialProof(libsnark::r1cs_ppzksnark_proof<libff::alt_bn128_pp> &proof, CredentialProof& p)
 {
-    CredentialProof p;
-
     p.A = libsnark::outputPointG1AffineAsHex(proof.g_A.g);
     p.A_p = libsnark::outputPointG1AffineAsHex(proof.g_A.h);
     p.B = libsnark::outputPointG2AffineAsHex(proof.g_B.g);
@@ -12,7 +10,6 @@ CredentialProof ExtractCredentialProof(libsnark::r1cs_ppzksnark_proof<libff::alt
     p.C_p = libsnark::outputPointG1AffineAsHex(proof.g_C.h);
     p.H = libsnark::outputPointG1AffineAsHex(proof.g_H);
     p.K = libsnark::outputPointG1AffineAsHex(proof.g_K);
-    return p;
 }
 
 VerificationKey ExtractVerificationKey(libsnark::r1cs_ppzksnark_verification_key<libff::alt_bn128_pp> &vk)
@@ -101,9 +98,10 @@ void ExportVerificationKey(VerificationKey &vk, const std::string &sol_path, con
     of.close();
 }
 
-void ExportProof(LibsnarkVerificationData &auth, std::string fname)
+void ExportProof(LibsnarkCredentialProof &auth, std::string fname)
 {
-    CredentialProof proof = ExtractCredentialProof(auth.proof);
+    CredentialProof proof;
+    ExtractCredentialProof(auth.proof, proof);
 
     std::ofstream f(fname);
     if (!f)

### 2018-05-13 include/proving/zkidVerificationStructs.h
Attribute fillers

@@ -4,6 +4,9 @@
 #include <array>
 #include <vector>
 #include <string>
+#include <climits>
+
+#define ZKID_CREDENTIAL_ATTRIBUTE_NUM 7
 
 enum VerificationErrorCode
 {
@@ -27,8 +30,9 @@ struct Credential
 
 struct AttributeRequest
 {
-    std::string lower_bound;
-    std::string upper_bound;
+    std::string lower_bound = "0x00";
+    std::string upper_bound = "0x7FFFFFFF";
+    int idx;
 };
 
 struct CredentialRequest

### 2018-05-13 src/network/ZkidRPCServer.cpp

@@ -2,9 +2,8 @@
 #include <cassert>
 
 ZkidRPCServer::ZkidRPCServer(jsonrpc::AbstractServerConnector &conn, ConfigRPCServerInterface *rpc_config) : AbstractZkidRPCServer(conn),
-                                                                                                _rpc_config(rpc_config)
+                                                                                                             _rpc_config(rpc_config)
 {
-    
 }
 
 Json::Value ZkidRPCServer::GenerateProofs(const Json::Value &credential_descs)
@@ -41,11 +40,25 @@ CredentialRequest ZkidRPCServer::CredentialRequestFromJson(const Json::Value &cr
     cred_desc.merkle_root_address = cred_json["merkle_root_address"].asString();
     cred_desc.k_bound = cred_json["k_bound"].asInt();
 
-    for(const Json::Value& attr_req_json : cred_json["requested_attributes"]){
+    for (const Json::Value &attr_req_json : cred_json["requested_attributes"])
+    {
         AttributeRequest attr_request;
         attr_request.lower_bound = attr_req_json["lower_bound"].asString();
         attr_request.upper_bound = attr_req_json["upper_bound"].asString();
+        attr_request.idx = attr_req_json["idx"].asInt();
         cred_desc.attribute_requests.push_back(attr_request);
+    }
+    
+    if (cred_desc.attribute_requests.size() < ZKID_CREDENTIAL_ATTRIBUTE_NUM)
+    {
+        for (int i = 0; i < ZKID_CREDENTIAL_ATTRIBUTE_NUM; i++)
+        {
+            if(cred_desc.attribute_requests.size() < i || cred_desc.attribute_requests[i].idx != i){
+                AttributeRequest r;
+                r.idx = i;
+                cred_desc.attribute_requests.push_back(r);
+            }
+        }
     }
 
     return cred_desc;

### 2018-05-13 src/network/ZkidService.cpp

@@ -32,18 +32,20 @@ bool ZkidService::GetProofForCredential(const CredentialRequest &cred, Credentia
     {
         auto cur_attribute = cred.attribute_requests[i];
         attribute_string +=
-            "attribute_index: " + std::to_string(i) + "\n" +
-            "lower_bound: " + cur_attribute.lower_bound + "\n" +
-            "upper_bound: " + cur_attribute.upper_bound + "\n";
+            "\t attribute_index: " + std::to_string(cur_attribute.idx) + "\n" +
+            "\t lower_bound: " + cur_attribute.lower_bound + "\n" +
+            "\t upper_bound: " + cur_attribute.upper_bound + "\n \n";
     }
 
     console->info("Recieved request for proof of credential: \n \
-        contract_salt: {0} \n \
-        merkle_root_address: {1} \n \ 
-        k_bound: {2} \n \
-        With Attributes: \n \
-        {3}",
-                  cred.contract_salt, cred.merkle_root_address, cred.k_bound, attribute_string);
+    ---------------------------------------------------------------------------- \n \
+    contract_salt: {0} \n \
+    merkle_root_address: {1} \n \ 
+    k_bound: {2} \n \
+    Attributes: \n \
+    {3}\
+    ---------------------------------------------------------------------------- \n",
+    cred.contract_salt, cred.merkle_root_address, cred.k_bound, attribute_string);
 
     return GenerateProofForCredential(cred, proof);
 }

### 2018-05-13 src/ui/js/site.js

@@ -1,5 +1,5 @@
 web3 = new Web3(new Web3.providers.HttpProvider("http://localhost:8545"));
-lottery_abi = JSON.parse('[ { "constant": false, "inputs": [ { "indexed": false, "name": "proofs", "type": "uint[]" } ], "name": "Join", "outputs": [], "payable": false, "type": "function", "credentials": [ { "contract_salt": "0xdeadbeef", "requested_attributes": [ { "attribute_idx": 0, "upper_bound": 0, "lower_bound": 0, "k_bound": 0, "description": "Confirms holder is over 18." }, { "attribute_idx": 1, "upper_bound": 100, "lower_bound": 18, "k_bound": 1, "description": "Confirms holder is American." } ] } ] } ]');
+lottery_abi = JSON.parse('[ { "constant": false, "inputs": [ { "indexed": false, "name": "proofs", "type": "uint[]" } ], "name": "Join", "outputs": [], "payable": false, "type": "function", "credentials": [ { "contract_salt": "0xdeadbeef", "k_bound": 1, "requested_attributes": [ { "idx": 0, "upper_bound": "0x7fffff", "lower_bound": "0x12", "description": "Confirms holder is over 18." }, { "idx": 1, "upper_bound": "0x01", "lower_bound": "0x01", "description": "Confirms holder is American." } ] } ] } ]');
 
 LotteryContract = web3.eth.contract(lottery_abi);
 contractInstance = LotteryContract.at("CONTRACT_ADDR");

### 2018-05-13 src/credentials/CredentialsManager.cpp
Fixed credentials

@@ -19,5 +19,5 @@ void CredentialsManager::LoadCredentials(){
                                                                             current_cred["secret_key"].asString(),
                                                                             current_cred["k"].asInt(),
                                                                             current_cred["contract_salt"].asString(),
-                                                                            current_cred["merkel_address"].asInt());}
+                                                                            current_cred["merkle_address"].asInt());}
 }

### 2018-05-13 src/ui/js/zkid.js

@@ -1,5 +1,5 @@
 
-issuer_abi = JSON.parse('[ { "constant": false, "inputs": [ { "indexed": false, "name": "proofs", "type": "uint[]" } ], "name": "Join", "outputs": [], "payable": false, "type": "function", "credentials": [ { "contract_salt": "0xdeadbeef", "k_bound": 0, "requested_attr": [ { "attribute_idx": 0, "upper_bound": 0, "lower_bound": 0, "description": "Confirms holder is over 18." }, { "attribute_idx": 1, "upper_bound": 100, "lower_bound": 18, "k_bound": 1, "description": "Confirms holder is American." } ] } ] } ]');
+issuer_abi = JSON.parse('[ { "constant": false, "inputs": [], "name": "getMerkleRootAddress", "outputs": [], "payable": false, "type": "function"}]');
 IssuerContract = web3.eth.contract(issuer_abi);
 currentBlock = null;
 
@@ -31,7 +31,7 @@ CredentialBlock.prototype.FetchCredentialProofs = function () {
     this.action.requiredCredentials = this.action.requiredCredentials.map((e) => {
         //ask each verifier contract for the address of its merkle root
         try {
-            var issuerContractInstance = IssuerContract.at(e["issuer_address"]);
+            var issuerContractInstance = IssuerContract.at(e["contract_salt"]);
             e["merkle_root_address"] = issuerContractInstance.getMerkleRootAddress().call();
         } catch (e) {
             e["merkle_root_address"] = "";

### 2018-05-14 include/proving/zkidProofGadget.h
Fixed JS

@@ -22,6 +22,7 @@ class zkidProofGadget
             libsnark_data->primary_input = _pb.primary_input();
         }
 
+        cred_proof.serial = HexStringFromLibsnarkBigint(libsnark_data->primary_input[1].as_bigint());
         
         ExtractCredentialProof(proof, cred_proof);
     }

### 2018-05-14 src/ui/js/zkid.js

@@ -4,7 +4,7 @@ IssuerContract = web3.eth.contract(issuer_abi);
 currentBlock = null;
 
 function ProofToBytes(proof) {
-    return [].concat(
+    return ([].concat(
         web3.utils.hexToBytes(proof["A"][0]),
         web3.utils.hexToBytes(proof["A"][1]),
         web3.utils.hexToBytes(proof["A_p"][0]),
@@ -22,7 +22,7 @@ function ProofToBytes(proof) {
         web3.utils.hexToBytes(proof["H"][0]),
         web3.utils.hexToBytes(proof["H"][1]),
         web3.utils.hexToBytes(proof["K"][0]),
-        web3.utils.hexToBytes(proof["K"][1]));
+        web3.utils.hexToBytes(proof["K"][1])), web3.utils.hexToBytes(proof["serial"]));
 }
 
 CredentialBlock.prototype.FetchCredentialProofs = function () {
@@ -43,12 +43,9 @@ CredentialBlock.prototype.FetchCredentialProofs = function () {
     client.GenerateProofs(this.action.requiredCredentials, (id, result) => {
         var generated_proofs = result["proofs"];
         this.highlightCredentials(generated_proofs);
-
         if (result["success"]) {
-            var proof_bytes = generated_proofs.reduce(function (acc, e) {
-                acc.concat(ProofToBytes(e));
-            }, []);
-            action.method(proof_bytes,generated_proofs.length);
+            proof_bytes,serial = ProofToBytes(e);                
+            action.method(proof_bytes,serial);
         } else {
             $("#msg-container").first().text("A proof could not be generated for one or more credentials.");
             $("#msg-container").show();

### 2018-05-14 src/ui/js/site.js
Stuff

@@ -1,5 +1,18 @@
 web3 = new Web3(new Web3.providers.HttpProvider("http://localhost:8545"));
-lottery_abi = JSON.parse('[ { "constant": false, "inputs": [ { "indexed": false, "name": "proofs", "type": "uint[]" } ], "name": "Join", "outputs": [], "payable": false, "type": "function", "credentials": [ { "contract_salt": "0xdeadbeef", "k_bound": 1, "requested_attributes": [ { "idx": 0, "upper_bound": "0x7fffff", "lower_bound": "0x12", "description": "Confirms holder is over 18." }, { "idx": 1, "upper_bound": "0x01", "lower_bound": "0x01", "description": "Confirms holder is American." } ] } ] } ]');
+
+lottery_abi = [ { "constant": false,
+                  "inputs": [ { "indexed": false, "name": "proofs", "type": "uint[]" } ],
+                  "name": "Join", "outputs": [], "payable": false, "type": "function",
+                  "credentials": [ { "contract_salt": "0xdeadbeef",
+                                     "k_bound": 1,
+                                     "requested_attributes": [
+                                         { "idx": 0, "upper_bound": "0x7fffff",
+                                           "lower_bound": "0x12",
+                                           "description": "Confirms holder is over 18." },
+                                         { "idx": 1, "upper_bound": "0x01",
+                                           "lower_bound": "0x01",
+                                           "description": "Confirms holder is American."
+                                         } ] } ] } ];
 
 LotteryContract = web3.eth.contract(lottery_abi);
 contractInstance = LotteryContract.at("CONTRACT_ADDR");
@@ -13,6 +26,6 @@ function OnJoinClick() {
 
 function PartialAppJoin(/* Insert non-proof arguments here*/) {
     return function (proof_bytes, serial) {
-        contractInstance.methods["Join"](proof_bytes,serial).send();
+        contractInstance.methods.Join(proof_bytes,serial).send();
     }
 }

### 2018-05-14 src/ui/js/zkid.js

@@ -44,7 +44,7 @@ CredentialBlock.prototype.FetchCredentialProofs = function () {
         var generated_proofs = result["proofs"];
         this.highlightCredentials(generated_proofs);
         if (result["success"]) {
-            proof_bytes,serial = ProofToBytes(e);                
+            proof_bytes,serial = ProofToBytes(e);
             action.method(proof_bytes,serial);
         } else {
             $("#msg-container").first().text("A proof could not be generated for one or more credentials.");

### 2018-05-14 src/ui/js/site.js
Added event callback

@@ -1,18 +1,25 @@
 web3 = new Web3(new Web3.providers.HttpProvider("http://localhost:8545"));
 
-lottery_abi = [ { "constant": false,
-                  "inputs": [ { "indexed": false, "name": "proofs", "type": "uint[]" } ],
-                  "name": "Join", "outputs": [], "payable": false, "type": "function",
-                  "credentials": [ { "contract_salt": "0xdeadbeef",
-                                     "k_bound": 1,
-                                     "requested_attributes": [
-                                         { "idx": 0, "upper_bound": "0x7fffff",
-                                           "lower_bound": "0x12",
-                                           "description": "Confirms holder is over 18." },
-                                         { "idx": 1, "upper_bound": "0x01",
-                                           "lower_bound": "0x01",
-                                           "description": "Confirms holder is American."
-                                         } ] } ] } ];
+lottery_abi = [{
+    "constant": false,
+    "inputs": [{ "indexed": false, "name": "proofs", "type": "uint[]" }],
+    "name": "Join", "outputs": [], "payable": false, "type": "function",
+    "credentials": [{
+        "contract_salt": "0xdeadbeef",
+        "k_bound": 1,
+        "requested_attributes": [
+            {
+                "idx": 0, "upper_bound": "0x7fffff",
+                "lower_bound": "0x12",
+                "description": "Confirms holder is over 18."
+            },
+            {
+                "idx": 1, "upper_bound": "0x01",
+                "lower_bound": "0x01",
+                "description": "Confirms holder is American."
+            }]
+    }]
+}];
 
 LotteryContract = web3.eth.contract(lottery_abi);
 contractInstance = LotteryContract.at("CONTRACT_ADDR");
@@ -25,7 +32,9 @@ function OnJoinClick() {
 /* Use partial application to supply non-proof arguments */
 
 function PartialAppJoin(/* Insert non-proof arguments here*/) {
-    return function (proof_bytes, serial) {
-        contractInstance.methods.Join(proof_bytes,serial).send();
+    return function (proof_bytes, serial, verify_cb,error_cb) {
+        contractInstance.methods.Join(proof_bytes, serial).send({"from":web3.eth.getCoinbase()},cb)
+        .on("Verify",verify_cb)
+        .on("Err",error_cb);
     }
 }

### 2018-05-14 src/ui/js/zkid.js

@@ -1,5 +1,5 @@
 
-issuer_abi = JSON.parse('[ { "constant": false, "inputs": [], "name": "getMerkleRootAddress", "outputs": [], "payable": false, "type": "function"}]');
+issuer_abi = JSON.parse('[ { "constant": false, "inputs": [], "name": "ipfs_hash", "outputs": [], "payable": false, "type": "function"}]');
 IssuerContract = web3.eth.contract(issuer_abi);
 currentBlock = null;
 
@@ -25,6 +25,14 @@ function ProofToBytes(proof) {
         web3.utils.hexToBytes(proof["K"][1])), web3.utils.hexToBytes(proof["serial"]));
 }
 
+
+CredentialBlock.prototype.showError = function (msg) {
+    $("#msg-container").first().text(msg);
+    $("#msg-container").show();
+    $("#return-button-container").show();
+}
+
+
 CredentialBlock.prototype.FetchCredentialProofs = function () {
     var client = new zkidclient("http://localhost:8383");
 
@@ -32,7 +40,7 @@ CredentialBlock.prototype.FetchCredentialProofs = function () {
         //ask each verifier contract for the address of its merkle root
         try {
             var issuerContractInstance = IssuerContract.at(e["contract_salt"]);
-            e["merkle_root_address"] = issuerContractInstance.getMerkleRootAddress().call();
+            e["merkle_root_address"] = issuerContractInstance.ipfs_hash().call();
         } catch (e) {
             e["merkle_root_address"] = "";
         } finally {
@@ -44,15 +52,17 @@ CredentialBlock.prototype.FetchCredentialProofs = function () {
         var generated_proofs = result["proofs"];
         this.highlightCredentials(generated_proofs);
         if (result["success"]) {
-            proof_bytes,serial = ProofToBytes(e);
-            action.method(proof_bytes,serial);
+            proof_bytes, serial = ProofToBytes(e);
+            action.method(proof_bytes, serial, function (result) {
+                OnReturn();
+            }, function (err) {
+                this.showError("Verification was unsuccessfuly for one or more credentials.")
+            });
         } else {
-            $("#msg-container").first().text("A proof could not be generated for one or more credentials.");
-            $("#msg-container").show();
-            $("#return-button-container").show();
+            this.showError("A proof could not be generated for one or more credentials.");
         }
-    }, function (code, msg) {
-        PostFetchError(code, msg);
+    }, (code, msg) => {
+        this.showError("Unable to connect to ZKID proof service.")
     });
 }
 
[…]

### 2018-05-14 src/ui/js/site.js
Verification Event Listeners

@@ -30,11 +30,17 @@ function OnJoinClick() {
 }
 
 /* Use partial application to supply non-proof arguments */
-
 function PartialAppJoin(/* Insert non-proof arguments here*/) {
-    return function (proof_bytes, serial, verify_cb,error_cb) {
+    return function (proof_bytes, serial, joined_cb,error_cb) {
         contractInstance.methods.Join(proof_bytes, serial).send({"from":web3.eth.getCoinbase()},cb)
-        .on("Verify",verify_cb)
-        .on("Err",error_cb);
+        .on("reciept",function(reciept){
+            if(reciept.events["Joined"] != undefined){
+                joined_cb();
+            }else if (reciept.events["Err"] != undefined){
+                error_cb();
+            }else{
+                console.log("Failed to capture a verifier event!")
+            }
+        })    
     }
 }

### 2018-05-14 src/ui/js/zkid.js

@@ -53,7 +53,7 @@ CredentialBlock.prototype.FetchCredentialProofs = function () {
         this.highlightCredentials(generated_proofs);
         if (result["success"]) {
             proof_bytes, serial = ProofToBytes(e);
-            action.method(proof_bytes, serial, function (result) {
+            action.method(proof_bytes, serial, function () {
                 OnReturn();
             }, function (err) {
                 this.showError("Verification was unsuccessfuly for one or more credentials.")

### 2018-05-14 paper/paper.tex
Spelling error

--- 2018-05-13 paper/paper.tex
@@
 \subsubsection{Credential Annotated ABI}
-The properly interface with the ZKID Service a dApp will have to provide an annotated ABI for its dependant contract(s).
-The required annotations describe the required credentials for a given method within the smart contract and will
-be used to propery construct public inputs and subsequently generate proofs for credentials. An annotated ABI function
+The properly interface with the ZKID Service a dApp would provide an annotated ABI for its dependant contract(s).
+The annotations describe the required credentials for a given method within the smart contract and will
+be used to communicate public inputs to the ZKID prooving service. An annotated ABI function
 would appear as follow:
-\begin{lstlisting}
-
-  {"constant":false,
-   "name":"Join",
-   "inputs":[],
-   "outputs":[],
-   "payable":false,
-   "type":"function","
-    "credentials":[
-      {"contract_salt":"0xdeadbeef",
-      "high_bound":255,
-      "low_bound":18,
-      "k_bound":1,
-      "description": "Confirms holder is over 18."
-      }
-    ]
-  }
-\end{lstlisting}
 
@@
 This can be accomplished very concisely by wrapping the credial-accepting method call with partially applied
-function. A full implementation of this exists in our example application and is depicted in [INSERT FIG NUMBER];
-\begin{lstlisting}
-function OnJoinClick() {
-  var credBlock = new CredentialBlock("Join", PartialAppJoin(), lottery_abi);
-    credBlock.display();
-}
+function.
 
-function PartialAppJoin(/* Insert non-proof arguments here*/) {
-  return function (proof_bytes) {
-    contractInstance.methods["Join"](/* Non-Proof Arguments*/ ,proof_bytes).send();
-  }
-}
-
-\end{lstlisting}
-
-In the above example, "Join" allowed a users to join a lottery if they have the required credentials. Originally, took a number of non-proof arguments. 
+The "Join" function in the provided example application is an example of how to properly provide the ZKID framework with a partially applied credential-enabled function.
+Originally, took a number of non-proof arguments.
 The credential enabled join now takes the non-proof arguments as well as proof arguments.

### 2018-05-14 include/proving/zkidProverImpl.h
Add export/inport

@@ -35,13 +35,49 @@ class zkidProverImpl : public zkidProofGadget, public zkidProver
  zkidProverImpl(int tree_depth, int attribute_size) : _zkid(_pb, tree_depth, attribute_size), attribute_size(attribute_size)
     {
       _zkid.generate_r1cs_constraints();
-      auto cs = _pb.get_constraint_system();
-      _keypair = std::make_shared<r1cs_ppzksnark_keypair<ppt>>
-        (r1cs_ppzksnark_keypair<ppt>(r1cs_ppzksnark_generator<ppt>(cs)));
-      _verification_key = r1cs_ppzksnark_verification_key<ppt>(_keypair->vk);
+      GenerateKeys();
     };
 
-    typedef Hash<FieldT> HashT;
+ zkidProverImpl(int tree_depth, int attribute_size, r1cs_ppzksnark_keypair<ppt> &keypair) : _zkid(_pb, tree_depth, attribute_size), attribute_size(attribute_size)
+  {
+    _zkid.generate_r1cs_constraints();
+    _keypair = std::make_shared<r1cs_ppzksnark_keypair<ppt>>(keypair);
+  };
+
+  typedef Hash<FieldT> HashT;
+
+    void GenerateKeys(){
+      _keypair = std::make_shared<r1cs_ppzksnark_keypair<ppt>>
+        (r1cs_ppzksnark_keypair<ppt>(r1cs_ppzksnark_generator<ppt>(_pb.get_constraint_system())));
+    }
+
+    void ExportKeys(std::string f){
+      std::ofstream vk_file(f + "/verifier.key");
+      std::ofstream pk_file(f + "/prover.key");
+      if(!vk_file || !pk_file)
+        std::cout << "File not found" << std::endl;
+
+      vk_file << _keypair->vk;
+      pk_file << _keypair->pk;
+      vk_file.close();
+      pk_file.close();
+    }
+
+    void ImportKeys(std::string f){
+      std::ifstream vk_file(f + "/verifier.key");
+      std::ifstream pk_file(f + "/prover.key");
+
+      if(!vk_file || !pk_file)
+        std::cout << "File not found" << std::endl;
+
+      r1cs_ppzksnark_verification_key<ppt> vk;
+      r1cs_ppzksnark_proving_key<ppt> pk;
+      vk_file >> vk;
+      pk_file >> pk;
+      vk_file.close();
+      pk_file.close();
[…]

### 2018-05-14 src/proving/keygen.cpp

@@ -1,0 +1,12 @@
+#include <libsnark/gadgetlib1/gadgets/hashes/sha256/sha256_gadget.hpp>
+#include <libff/algebra/curves/alt_bn128/alt_bn128_pp.hpp>
+#include "proving/zkidProverImpl.h"
+#include "util/zkid_helpers.h"
+
+int main(int argc, char* argv[])
+{
+  int tree_depth = atoi(argv[1]);
+  libff::alt_bn128_pp::init_public_params();
+  zkidProverImpl<sha256_two_to_one_hash_gadget> zkid(tree_depth, 32);
+  zkid.ExportKeys(argv[2]);
+}

### 2018-05-14 src/contracts/deployment/deploy.js
Added deployment

@@ -1,0 +1,59 @@
+
+Web3 = require ("web3")
+fs = require('fs')
+
+web3 = new Web3(new Web3.providers.HttpProvider("http://localhost:8545"));
+fs.readFile('../verifier.sol', function (err, data) {
+    web3.eth.compile.solidity(data).then(function (result) {
+        var pairingLibrary = new web3.eth.Contract(result["Pairing"]["info"]["abiDefinition"]);
+        pairingLibrary.deploy({
+            "data": result["Pairing"]["code"]
+        }).send({
+            "from": web3.eth.getCoinbase(),
+            gas: 6000000
+        }).then(function (paringInstance) {
+            var verifierLinkedCode = result["Verifier"]["code"].replace("__Pairing______", paringInstance.options.address);
+            var verifierLibrary = new web3.eth.Contract(result["Verifier"]["info"]["abiDefinitions"]);
+            verifierLibrary.deploy({
+                "data": verifierLinkedCode
+            }).send({
+                "from": web3.eth.getCoinbase(),
+                gas: 6000000
+            }).then(function (verifierInstance) {
+                DeployExampleContract(verifierInstance.options.address);
+            });
+        });
+    });
+});
+
+function DeployExampleContract(verifier_contract_address) {
+    fs.readFile('../ExampleContract.sol', function (err, data) {
+        web3.eth.compile.solidity(data).then(function (result) {
+            var linked_code = result["code"].replace("__Verifier______", verifier_contract_address);
+            var lotteryContract = new web3.eth.Contract(result["ExampleContract"]["info"]["abiDefinition"]);
+            loterryContract.deploy({
+                "data": result["ExampleContract"]["code"]
+            }).send({
+                "from": web3.eth.getCoinbase(),
+                gas: 6000000
+            }).then(function (exampleContractInstance) {
+                console.log("ExampleContract: " + exampleContractInstance.options.address);
+            });
+        })
+    });
+}
+
+fs.readFile('../ExampleIssuer.sol', function (err, data) {
+    web3.eth.compile.solidity(data).then(function (result) {
+        var issuerContract = new web3.eth.Contract(result["info"]["abiDefinition"]);
+        loterryContract.deploy({
+            "data": result["code"]
+        }).send({
+            "from": web3.eth.getCoinbase(),
+            gas: 6000000
+        }).then(function (exampleIssuerInstance) {
+            console.log("ExampleIssuer: " + exampleIssuerInstance.options.address);
+        });
+    })
+});
+

### 2018-05-14 include/proving/zkidProverImpl.h
Load keys from file

@@ -38,10 +38,10 @@ class zkidProverImpl : public zkidProofGadget, public zkidProver
       GenerateKeys();
     };
 
- zkidProverImpl(int tree_depth, int attribute_size, r1cs_ppzksnark_keypair<ppt> &keypair) : _zkid(_pb, tree_depth, attribute_size), attribute_size(attribute_size)
+ zkidProverImpl(int tree_depth, int attribute_size,  std::string key_path) : _zkid(_pb, tree_depth, attribute_size), attribute_size(attribute_size)
   {
     _zkid.generate_r1cs_constraints();
-    _keypair = std::make_shared<r1cs_ppzksnark_keypair<ppt>>(keypair);
+    ImportKeys(key_path);
   };
 
   typedef Hash<FieldT> HashT;

### 2018-05-14 src/configuration/ZkidConfiguration.cpp

@@ -29,3 +29,7 @@ std::string ZkidConfiguration::GetIPFSClientIP(){
 int ZkidConfiguration::GetIPFSClientPort(){
     return _config["ipfs_client_port"].asInt();
 }
+
+std::string ZkidConfiguration::GetKeyPath(){
+  return _config["zk_key_dir"].asString();
+}

### 2018-05-14 src/network/ZkidService.cpp

@@ -9,7 +9,6 @@ ZkidService::ZkidService(ConfigZkidServiceInterface *service_config, Credentials
     _rpc_server = std::make_shared<ZkidRPCServer>(_http_server, _service_config);
     if (dynamic_cast<jsonrpc::AbstractServerConnector *>(&_http_server)->GetHandler() == NULL)
         exit(0);
-
     _rpc_server->SetProofHandler(this);
 };
 
@@ -75,7 +74,7 @@ bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_reque
         return false;
     }
 
-    zkidProverImpl<sha256_two_to_one_hash_gadget> prover(merkle_path.size(), 32);
+    zkidProverImpl<sha256_two_to_one_hash_gadget> prover(merkle_path.size(), 32, _service_config->GetKeyPath());
 
     ProofRequest proof_request = ConstructProofRequest(cred_request, cred, merkle_root, merkle_path);
 

### 2018-05-14 include/configuration/ZkidConfiguration.h
Fix config class

@@ -21,6 +21,7 @@ public:
   //ConfigProverInterface
   std::string GetMerkleTreeEndpoint(const std::string &issuer);
 
+  std::string GetKeyPath();
 
   //ConfigIPFSInterfance
   std::string GetIPFSClientIP();

### 2018-05-14 src/network/ZkidService.cpp
Fix merkle path segfault bug

@@ -56,24 +56,26 @@ int ZkidService::GetPort()
 
 bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_request, CredentialProof &proof)
 {
-
     const std::string issuer_address = cred_request.contract_salt;
     if (!_cred_manager->HasCredential(issuer_address))
     {
         console->error("User does not have a credential from: {0}", issuer_address);
         return false;
     }
-
     Credential cred = _cred_manager->GetCredential(issuer_address);
+   
     std::vector<std::string> merkle_path;
-    std::string merkle_root = _mt_provider->GetMerklePath(cred_request.merkle_root_address, cred.merkle_address, merkle_path);
 
+    if(cred_request.merkle_root_address.empty()){
+      console->error("Merkle address blank");
+      return false;
+    }
+    std::string merkle_root = _mt_provider->GetMerklePath(cred_request.merkle_root_address, cred.merkle_address, merkle_path);
     if (merkle_path.empty())
     {
         console->error("Enable to get merkle path from: {0}", cred_request.merkle_root_address);
         return false;
     }
-
     zkidProverImpl<sha256_two_to_one_hash_gadget> prover(merkle_path.size(), 32, _service_config->GetKeyPath());
 
     ProofRequest proof_request = ConstructProofRequest(cred_request, cred, merkle_root, merkle_path);

### 2018-05-14 src/network/zkidIPFSGateway.cpp

@@ -45,6 +45,7 @@ std::string zkidIPFSGateway::GetMerklePath(const std::string &merkle_address, si
     }catch(std::runtime_error& e){
         //unable to get files
         path.clear();
+        return "";
     }
 }
 

### 2018-05-14 run_service.cpp
Added Merkle Tree

@@ -1,3 +1,5 @@
+#include <chrono>
+#include <thread>
 #include "cxxopts/cxxopts.hpp"
 #include "network/ZkidService.h"
 #include "configuration/ZkidConfiguration.h"
@@ -7,13 +9,21 @@
 int main(int argc, char **argv)
 {
     cxxopts::Options options("ZKID Service", "Zero-Knowledge identity proof generation service and credential manager for the Ethereum Blockcahin.");
-    options.add_options()("f,configuration-file", "Path to file where service configuration file is stored", cxxopts::value<std::string>());
-    options.add_options()("l,ipfs-flag", "Launch local ipfs service", cxxopts::value<bool>());
+    options.add_options()("f,configuration-file", "Path to file where service configuration file is stored", cxxopts::value<std::string>()->default_value(""));
+    options.add_options()("l,ipfs-flag", "Launch local ipfs service", cxxopts::value<bool>()->default_value("false"));
+    options.add_options()("u,upload-merke-tree","Uploads a merkle tree at given file",cxxopts::value<std::string>()->default_value(""));
     auto result = options.parse(argc, argv);
 
     IPFSServiceController ipfs_service;
 
-    ZkidConfiguration config(result["f"].as<std::string>());
+    std::string config_file_path = result["f"].as<std::string>();
+
+    if(config_file_path.empty()){
+        ZkidService::console->error("Please supply a configuration file with the -f option");
+        return 0;
+    }
+
+    ZkidConfiguration config(config_file_path);
     CredentialsManager cred_manager(&config);
     zkidIPFSGateway zkidIPFSGateway(&config);
 
@@ -28,6 +38,20 @@ int main(int argc, char **argv)
         {
             service.console->info("Starting IPFS daemon...", service.GetPort());
             ipfs_service.StartService();
+            std::this_thread::sleep_for(std::chrono::seconds(1));
+        }
+        std::string merkle_file_path = result["u"].as<std::string>();
+
+        if(!merkle_file_path.empty()){
+            Json::Value v = JsonObjectFromFile(merkle_file_path);
+
+            std::vector<std::string> tree;
+            for(int i = 0; i < v["merkle_proof"].size(); i++){
+                tree.push_back(v["merkle_proof"][i].asString());
+            }
+
+            std::string merkle_tree_address = zkidIPFSGateway.PutMerkleTree(tree);
[…]

### 2018-05-14 upload_merkle_tree.cpp

@@ -1,5 +1,0 @@
-#include "network/"
-
-int main(int argc, int argv){
-
-}

### 2018-05-14 src/network/ZkidService.cpp
Set up contract deployment

@@ -63,7 +63,7 @@ bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_reque
         return false;
     }
     Credential cred = _cred_manager->GetCredential(issuer_address);
-   
+
     std::vector<std::string> merkle_path;
 
     if(cred_request.merkle_root_address.empty()){

### 2018-05-14 src/proving/keygen.cpp
Implement key generation and verifier export

@@ -9,4 +9,7 @@ int main(int argc, char* argv[])
   libff::alt_bn128_pp::init_public_params();
   zkidProverImpl<sha256_two_to_one_hash_gadget> zkid(tree_depth, 32);
   zkid.ExportKeys(argv[2]);
+  auto vk_pp = zkid.GetVerificationKey();
+  VerificationKey vk = ExtractVerificationKey(vk_pp);
+  ExportVerificationKey(vk, "test/res/verification.sol.tmpl", std::string(argv[2])+"/verification.sol");
 }

### 2018-05-14 include/network/ZkidRPCServer.h
RPC Tests

@@ -17,7 +17,7 @@ class ZkidRPCServer : public AbstractZkidRPCServer
 {
 
 public:
-  ZkidRPCServer(jsonrpc::AbstractServerConnector &conn, ConfigRPCServerInterface *rpc_config);
+  ZkidRPCServer(jsonrpc::AbstractServerConnector& conn, ConfigRPCServerInterface *rpc_config);
   Json::Value GenerateProofs(const Json::Value &credential_descriptions);
   void SetProofHandler(ZkidProofHandler *listener);
 

### 2018-05-14 include/proving/zkidVerificationStructs.h

@@ -16,7 +16,7 @@ enum VerificationErrorCode
 struct Credential
 {
     Credential(){};
-    Credential(std::string a, std::string key, int _k, std::string cs, size_t ma) : attributes(a),
+    Credential(std::string a, std::string key, uint _k, std::string cs, size_t ma) : attributes(a),
                                                                          k(_k),
                                                                          contract_salt(cs),
                                                                          secret_key(key),
@@ -24,7 +24,7 @@ struct Credential
     std::string secret_key;
     std::string contract_salt;
     std::string attributes;
-    int k;
+    uint k;
     size_t merkle_address;
 };
 
@@ -40,7 +40,7 @@ struct CredentialRequest
     std::string contract_salt;
     std::string merkle_root_address;
     std::vector<AttributeRequest> attribute_requests;
-    int k_bound;
+    uint k_bound;
 };
 
 struct CredentialProof

### 2018-05-14 src/network/ZkidRPCServer.cpp

@@ -1,7 +1,7 @@
 #include "network/ZkidRPCServer.h"
 #include <cassert>
 
-ZkidRPCServer::ZkidRPCServer(jsonrpc::AbstractServerConnector &conn, ConfigRPCServerInterface *rpc_config) : AbstractZkidRPCServer(conn),
+ZkidRPCServer::ZkidRPCServer(jsonrpc::AbstractServerConnector& conn, ConfigRPCServerInterface *rpc_config) : AbstractZkidRPCServer(conn),
                                                                                                              _rpc_config(rpc_config)
 {
 }
@@ -38,7 +38,7 @@ CredentialRequest ZkidRPCServer::CredentialRequestFromJson(const Json::Value &cr
     CredentialRequest cred_desc;
     cred_desc.contract_salt = cred_json["contract_salt"].asString();
     cred_desc.merkle_root_address = cred_json["merkle_root_address"].asString();
-    cred_desc.k_bound = cred_json["k_bound"].asInt();
+    cred_desc.k_bound = cred_json["k_bound"].asUInt();
 
     for (const Json::Value &attr_req_json : cred_json["requested_attributes"])
     {

### 2018-05-14 src/network/ZkidService.cpp

@@ -73,14 +73,16 @@ bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_reque
     std::string merkle_root = _mt_provider->GetMerklePath(cred_request.merkle_root_address, cred.merkle_address, merkle_path);
     if (merkle_path.empty())
     {
-        console->error("Enable to get merkle path from: {0}", cred_request.merkle_root_address);
+        console->error("Unable to get merkle path from: {0}", cred_request.merkle_root_address);
         return false;
     }
+
     zkidProverImpl<sha256_two_to_one_hash_gadget> prover(merkle_path.size(), 32, _service_config->GetKeyPath());
 
-    ProofRequest proof_request = ConstructProofRequest(cred_request, cred, merkle_root, merkle_path);
+    /*ProofRequest proof_request = ConstructProofRequest(cred_request, cred, merkle_root, merkle_path);
 
-    return prover.GetCredentialProof(proof_request, proof);
+    return prover.GetCredentialProof(proof_request, proof);*/
+    return false;
 }
 
 ProofRequest ConstructProofRequest(const CredentialRequest &req, const Credential &cred, const std::string &merkle_root, const std::vector<std::string> merkle_path)

### 2018-05-14 test/authentication/ProofFromCredentialRequest.cpp

@@ -1,0 +1,40 @@
+#include <gtest/gtest.h>
+#include "network/ZkidRPCServer.h"
+#include "network/ZkidService.h"
+#include "network/zkidIPFSGateway.h"
+#include "configuration/ZkidConfiguration.h"
+#include "network/IPFSServiceController.h"
+
+TEST(TestProofRPC, TestProofFromCredentialRequest)
+{
+    ZkidConfiguration config("test/res/zkid_test_config.json");
+
+    CredentialsManager cred_manager(&config);
+    cred_manager.LoadCredentials();
+    zkidIPFSGateway zkidIPFSGateway(&config);
+    ZkidService service(&config, &cred_manager, &zkidIPFSGateway);
+
+
+    IPFSServiceController ipfs_service;
+
+    ipfs_service.StartService();
+
+    jsonrpc::HttpServer http_server(0);
+
+    AttributeRequest at_req;
+    at_req.idx = 0;
+    at_req.lower_bound = "00";
+    at_req.upper_bound = "aa";
+
+    CredentialRequest req;
+    req.k_bound = 1791871409;
+    req.merkle_root_address = "QmWgxfXhs2rovrqDKoNSprrWpZKZiF9edUTVd7U2q3BR1M";
+    req.contract_salt = "9f616104a4d4cafda53f8ccf95c5136684628fe0970f34dff50db8";
+    req.attribute_requests.push_back(at_req);
+    
+
+    CredentialProof p;
+    ASSERT_TRUE(service.GetProofForCredential(req, p));
+
+    ipfs_service.StopService();
+}

### 2018-05-14 test/authentication/zkMerkelTreeAuthenticatorTest.cpp

@@ -1,4 +1,4 @@
-#include <gtest/gtest.h>
+/*#include <gtest/gtest.h>
 #include <libsnark/gadgetlib1/gadgets/hashes/sha256/sha256_gadget.hpp>
 #include <libff/algebra/curves/alt_bn128/alt_bn128_pp.hpp>
 #include "proving/zkidProverImpl.h"
@@ -64,3 +64,4 @@ TEST(zkIDTest, TestVerifyFail){
   ASSERT_FALSE(verified);
 }
 
+*/

### 2018-05-14 include/network/ZkidRPCServer.h
Credential tests

@@ -10,7 +10,7 @@
 class ZkidProofHandler
 {
 public:
-    virtual bool GetProofForCredential(const CredentialRequest &cred, CredentialProof& proof) = 0;
+    virtual bool GetProofForCredential(CredentialRequest &cred, CredentialProof& proof) = 0;
 };
 
 class ZkidRPCServer : public AbstractZkidRPCServer

### 2018-05-14 include/proving/zkidProverImpl.h

@@ -32,13 +32,13 @@ template <template <typename> typename Hash>
 class zkidProverImpl : public zkidProofGadget, public zkidProver
 {
   public:
- zkidProverImpl(int tree_depth, int attribute_size) : _zkid(_pb, tree_depth, attribute_size), attribute_size(attribute_size)
+ zkidProverImpl(int tree_depth, int attr_size) : _zkid(_pb, tree_depth, attr_size), attribute_size(attr_size)
     {
       _zkid.generate_r1cs_constraints();
       GenerateKeys();
     };
 
- zkidProverImpl(int tree_depth, int attribute_size,  std::string key_path) : _zkid(_pb, tree_depth, attribute_size), attribute_size(attribute_size)
+ zkidProverImpl(int tree_depth, int attr_size,  std::string key_path) : _zkid(_pb, tree_depth, attr_size), attribute_size(attr_size)
   {
     _zkid.generate_r1cs_constraints();
     ImportKeys(key_path);
@@ -74,6 +74,7 @@ class zkidProverImpl : public zkidProofGadget, public zkidProver
       r1cs_ppzksnark_proving_key<ppt> pk;
       vk_file >> vk;
       pk_file >> pk;
+
       vk_file.close();
       pk_file.close();
       _keypair.reset(new r1cs_ppzksnark_keypair<ppt>(std::move(pk), std::move(vk)));

### 2018-05-14 include/proving/zkidVerificationStructs.h

@@ -30,8 +30,8 @@ struct Credential
 
 struct AttributeRequest
 {
-    std::string lower_bound = "0x00";
-    std::string upper_bound = "0x7FFFFFFF";
+    std::string lower_bound = "00000000";
+    std::string upper_bound = "7fffffff";
     int idx;
 };
 

### 2018-05-14 src/network/ZkidRPCServer.cpp

@@ -49,18 +49,6 @@ CredentialRequest ZkidRPCServer::CredentialRequestFromJson(const Json::Value &cr
         cred_desc.attribute_requests.push_back(attr_request);
     }
     
-    if (cred_desc.attribute_requests.size() < ZKID_CREDENTIAL_ATTRIBUTE_NUM)
-    {
-        for (int i = 0; i < ZKID_CREDENTIAL_ATTRIBUTE_NUM; i++)
-        {
-            if(cred_desc.attribute_requests.size() < i || cred_desc.attribute_requests[i].idx != i){
-                AttributeRequest r;
-                r.idx = i;
-                cred_desc.attribute_requests.push_back(r);
-            }
-        }
-    }
-
     return cred_desc;
 }
 

### 2018-05-14 src/network/ZkidService.cpp

@@ -23,8 +23,21 @@ void ZkidService::Stop()
     console->info("Stopped zkid service on port {0}.", _service_config->GetServicePort());
 }
 
-bool ZkidService::GetProofForCredential(const CredentialRequest &cred, CredentialProof &proof)
+bool ZkidService::GetProofForCredential(CredentialRequest &cred, CredentialProof &proof)
 {
+    if (cred.attribute_requests.size() < ZKID_CREDENTIAL_ATTRIBUTE_NUM)
+    {
+        for (int i = 0; i < ZKID_CREDENTIAL_ATTRIBUTE_NUM; i++)
+        {
+            if (cred.attribute_requests.size() < i || cred.attribute_requests[i].idx != i)
+            {
+                AttributeRequest r;
+                r.idx = i;
+                cred.attribute_requests.push_back(r);
+            }
+        }
+    }
+
     std::string attribute_string;
 
     for (int i = 0; i < cred.attribute_requests.size(); i++)
@@ -44,7 +57,7 @@ bool ZkidService::GetProofForCredential(const CredentialRequest &cred, Credentia
     Attributes: \n \
     {3}\
     ---------------------------------------------------------------------------- \n",
-    cred.contract_salt, cred.merkle_root_address, cred.k_bound, attribute_string);
+                  cred.contract_salt, cred.merkle_root_address, cred.k_bound, attribute_string);
 
     return GenerateProofForCredential(cred, proof);
 }
@@ -63,12 +76,13 @@ bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_reque
         return false;
     }
     Credential cred = _cred_manager->GetCredential(issuer_address);
-   
+
     std::vector<std::string> merkle_path;
 
-    if(cred_request.merkle_root_address.empty()){
-      console->error("Merkle address blank");
-      return false;
+    if (cred_request.merkle_root_address.empty())
+    {
+        console->error("Merkle address blank");
+        return false;
     }
     std::string merkle_root = _mt_provider->GetMerklePath(cred_request.merkle_root_address, cred.merkle_address, merkle_path);
     if (merkle_path.empty())
@@ -77,12 +91,11 @@ bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_reque
         return false;
     }
 
-    zkidProverImpl<sha256_two_to_one_hash_gadget> prover(merkle_path.size(), 32, _service_config->GetKeyPath());
[…]

### 2018-05-14 test/authentication/ProofFromCredentialRequest.cpp

@@ -7,13 +7,13 @@
 
 TEST(TestProofRPC, TestProofFromCredentialRequest)
 {
+    libff::alt_bn128_pp::init_public_params();
     ZkidConfiguration config("test/res/zkid_test_config.json");
 
     CredentialsManager cred_manager(&config);
     cred_manager.LoadCredentials();
     zkidIPFSGateway zkidIPFSGateway(&config);
     ZkidService service(&config, &cred_manager, &zkidIPFSGateway);
-
 
     IPFSServiceController ipfs_service;
 
@@ -23,15 +23,14 @@ TEST(TestProofRPC, TestProofFromCredentialRequest)
 
     AttributeRequest at_req;
     at_req.idx = 0;
-    at_req.lower_bound = "00";
-    at_req.upper_bound = "aa";
+    at_req.lower_bound = "00000000";
+    at_req.upper_bound = "7fffffff";
 
     CredentialRequest req;
     req.k_bound = 1791871409;
     req.merkle_root_address = "QmWgxfXhs2rovrqDKoNSprrWpZKZiF9edUTVd7U2q3BR1M";
     req.contract_salt = "9f616104a4d4cafda53f8ccf95c5136684628fe0970f34dff50db8";
     req.attribute_requests.push_back(at_req);
-    
 
     CredentialProof p;
     ASSERT_TRUE(service.GetProofForCredential(req, p));

### 2018-05-14 include/proving/zkidProverImpl.h
Add import/export test

@@ -35,13 +35,16 @@ class zkidProverImpl : public zkidProofGadget, public zkidProver
  zkidProverImpl(int tree_depth, int attribute_size) : _zkid(_pb, tree_depth, attribute_size), attribute_size(attribute_size)
     {
       _zkid.generate_r1cs_constraints();
+      std::cout << "Generating Keypairs" << std::endl;
       GenerateKeys();
     };
 
  zkidProverImpl(int tree_depth, int attribute_size,  std::string key_path) : _zkid(_pb, tree_depth, attribute_size), attribute_size(attribute_size)
   {
     _zkid.generate_r1cs_constraints();
+    std::cout << "Importing keys" << std::endl;
     ImportKeys(key_path);
+    std::cout << "Done!" << std::endl;
   };
 
   typedef Hash<FieldT> HashT;
@@ -80,7 +83,7 @@ class zkidProverImpl : public zkidProofGadget, public zkidProver
     }
 
     bool GetCredentialProof(ProofRequest &proof_req, CredentialProof &data,
-                             LibsnarkCredentialProof *libsnark_data = nullptr)
+                             LibsnarkCredentialProof &libsnark_data)
     {
         //Pb variables
         const size_t digest_len = HashT::get_digest_len();
@@ -104,6 +107,7 @@ class zkidProverImpl : public zkidProofGadget, public zkidProver
         bit_vector_from_string(attributes_bv, proof_req.attributes);
         bit_vector_from_string(upper_bounds_bv, proof_req.upper_bounds);
         bit_vector_from_string(lower_bounds_bv, proof_req.lower_bounds);
+
         //Fills in the variables on the protoboard
         _zkid.generate_r1cs_witness(secret_key_bv,
                                     upper_bounds_bv,
@@ -117,7 +121,7 @@ class zkidProverImpl : public zkidProofGadget, public zkidProver
                                     address,
                                     auth_path);
 
-        pb_variable_array<FieldT> k_bound_bits(_zkid.salt_kbound_bits.end() - 32, _zkid.salt_kbound_bits.end());
+        //pb_variable_array<FieldT> k_bound_bits(_zkid.salt_kbound_bits.end() - 32, _zkid.salt_kbound_bits.end());
 
         //Generate a authentication proof if the pb is satisified.
         if (!_pb.is_satisfied())
[…]

### 2018-05-14 src/network/ZkidService.cpp

@@ -79,8 +79,8 @@ bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_reque
     zkidProverImpl<sha256_two_to_one_hash_gadget> prover(merkle_path.size(), 32, _service_config->GetKeyPath());
 
     ProofRequest proof_request = ConstructProofRequest(cred_request, cred, merkle_root, merkle_path);
-
-    return prover.GetCredentialProof(proof_request, proof);
+    LibsnarkCredentialProof libsnark_data;
+    return prover.GetCredentialProof(proof_request, proof, libsnark_data);
 }
 
 ProofRequest ConstructProofRequest(const CredentialRequest &req, const Credential &cred, const std::string &merkle_root, const std::vector<std::string> merkle_path)

### 2018-05-14 test/authentication/zkMerkelTreeAuthenticatorTest.cpp

@@ -5,16 +5,17 @@
 #include "util/zkid_helpers.h"
 
 
-#define M_TREE_LENGTH 32
+#define M_TREE_LENGTH 8
 
 TEST(zkIDTest, TestProofGeneration){
   ProofRequest proof;
   CredentialProof verification_data;
+  LibsnarkCredentialProof libsnrak_data;
 
   ProofRequestFromJson("test/res/test_credential_proof.json", proof);
   libff::alt_bn128_pp::init_public_params();
   zkidProverImpl<sha256_two_to_one_hash_gadget> authenticator(proof.path.size(), 32);
-  bool verifiable = authenticator.GetCredentialProof(proof, verification_data);
+  bool verifiable = authenticator.GetCredentialProof(proof, verification_data, libsnrak_data);
   ASSERT_TRUE(verifiable);
 }
 
@@ -27,7 +28,7 @@ TEST(zkIDTest, TestVerify){
   zkidProverImpl<sha256_two_to_one_hash_gadget> authenticator(proof.path.size(), 32);
 
   LibsnarkCredentialProof libsnark_data;
-  authenticator.GetCredentialProof(proof, verification_data, &libsnark_data);
+  authenticator.GetCredentialProof(proof, verification_data, libsnark_data);
   const bool verified = r1cs_ppzksnark_verifier_strong_IC<libff::alt_bn128_pp>(authenticator.GetVerificationKey(),
                                                          libsnark_data.primary_input,
                                                          libsnark_data.proof);
@@ -39,12 +40,29 @@ TEST(zkIDTest, TestVerify){
 
 
 TEST(zkIDTest, TestExportVerifier){
+  libff::alt_bn128_pp::init_public_params();
   zkidProverImpl<sha256_two_to_one_hash_gadget> zkid(M_TREE_LENGTH, 32);
-
   auto vk_pp = zkid.GetVerificationKey();
   VerificationKey vk = ExtractVerificationKey(vk_pp);
 
   ExportVerificationKey(vk, "test/res/verification.sol.tmpl", "test/res/verification.sol");
+
+}
+
+TEST(zkIDTest, TestImportKeys){
+  ProofRequest proof;
+  CredentialProof verification_data;
+
+  ProofRequestFromJson("test/res/test_credential_proof.json", proof);
+  libff::alt_bn128_pp::init_public_params();
[…]

### 2018-05-14 src/network/ZkidService.cpp
Working request proof

@@ -91,7 +91,7 @@ bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_reque
         return false;
     }
 
-    zkidProverImpl<sha256_two_to_one_hash_gadget> prover(merkle_path.size(), 32);
+    zkidProverImpl<sha256_two_to_one_hash_gadget> prover(merkle_path.size(), 32, _service_config->GetKeyPath());
 
     ProofRequest proof_request = ConstructProofRequest(cred_request, cred, merkle_root, merkle_path);
     LibsnarkCredentialProof libsnark_data;

### 2018-05-14 test/authentication/ProofFromCredentialRequest.cpp

@@ -21,16 +21,21 @@ TEST(TestProofRPC, TestProofFromCredentialRequest)
 
     jsonrpc::HttpServer http_server(0);
 
-    AttributeRequest at_req;
-    at_req.idx = 0;
-    at_req.lower_bound = "00000000";
-    at_req.upper_bound = "7fffffff";
-
     CredentialRequest req;
     req.k_bound = 1791871409;
     req.merkle_root_address = "QmWgxfXhs2rovrqDKoNSprrWpZKZiF9edUTVd7U2q3BR1M";
     req.contract_salt = "9f616104a4d4cafda53f8ccf95c5136684628fe0970f34dff50db8";
-    req.attribute_requests.push_back(at_req);
+    std::string upper_bound = "afa0136fea32ccd3f72f9ca603e4bf975e882f739b2d6dff63b70bb7";
+    std::string lower_bound = "02e7380c0a29d5fc4ad06a20b6c75ebbc139ca98183976d24be332b5";
+
+    for (int i = 0; i < 7; i++)
+    {
+        AttributeRequest at_req;
+        at_req.idx = i;
+        at_req.lower_bound = lower_bound.substr(i*8,8);
+        at_req.upper_bound = upper_bound.substr(i*8,8);;
+        req.attribute_requests.push_back(at_req);
+    }
 
     CredentialProof p;
     ASSERT_TRUE(service.GetProofForCredential(req, p));

### 2018-05-14 src/network/ZkidService.cpp
Working Reactive UI

@@ -95,7 +95,16 @@ bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_reque
 
     ProofRequest proof_request = ConstructProofRequest(cred_request, cred, merkle_root, merkle_path);
     LibsnarkCredentialProof libsnark_data;
-    return prover.GetCredentialProof(proof_request, proof, libsnark_data);
+    if (prover.GetCredentialProof(proof_request, proof, libsnark_data))
+    {
+        console->info("Successfully generated proof for: {0}", issuer_address);
+        return true;
+    }
+    else
+    {
+        console->error("Failed to generate proof for: {0}", issuer_address);
+        return false;
+    }
 }
 
 ProofRequest ConstructProofRequest(const CredentialRequest &req, const Credential &cred, const std::string &merkle_root, const std::vector<std::string> merkle_path)

### 2018-05-14 src/ui/js/zkid.js

@@ -39,10 +39,11 @@ CredentialBlock.prototype.FetchCredentialProofs = function () {
     this.action.requiredCredentials = this.action.requiredCredentials.map((e) => {
         //ask each verifier contract for the address of its merkle root
         try {
-            var issuerContractInstance = IssuerContract.at(e["contract_salt"]);
-            e["merkle_root_address"] = issuerContractInstance.ipfs_hash().call();
+            //var issuerContractInstance = IssuerContract.at(e["contract_salt"]);
+            e["merkle_root_address"] = "QmWgxfXhs2rovrqDKoNSprrWpZKZiF9edUTVd7U2q3BR1M";
+           //e["merkle_root_address"] = issuerContractInstance.ipfs_hash().call();
         } catch (e) {
-            e["merkle_root_address"] = "";
+            e["merkle_root_address"] = "QmWgxfXhs2rovrqDKoNSprrWpZKZiF9edUTVd7U2q3BR1M";
         } finally {
             return e;
         }
@@ -52,7 +53,7 @@ CredentialBlock.prototype.FetchCredentialProofs = function () {
         var generated_proofs = result["proofs"];
         this.highlightCredentials(generated_proofs);
         if (result["success"]) {
-            proof_bytes, serial = ProofToBytes(e);
+            var proof_bytes, serial = ProofToBytes(e);
             action.method(proof_bytes, serial, function () {
                 OnReturn();
             }, function (err) {
@@ -67,10 +68,10 @@ CredentialBlock.prototype.FetchCredentialProofs = function () {
 }
 
 CredentialBlock.prototype.highlightCredentials = function (generated_proofs) {
-    $("#credential_table").find("tr:not(:first-child)").each(function () {
+    $("#credential_table").find("> tr:not(:first-child)").each(function () {
         var issuer_addr = $(this).find(">:first-child").text();
         var was_generated = generated_proofs == null ? false : generated_proofs.reduce(function (acc, e) {
-            return acc ? true : e["issuer_address"] === issuer_addr;
+            return acc ? true : e["contract_salt"] === issuer_addr;
         }, false);
         if (was_generated)
             $(this).animate({ backgroundColor: "#C8E6C9" }, 500);
@@ -97,11 +98,14 @@ CredentialBlock.prototype.display = function () {
 
             console.log(current_cred);
             for (var i = 0; i < current_cred["requested_attributes"].length; i++) {
+
                 var current_attr = current_cred["requested_attributes"][i];
-                var desc_row = document.createElement("tr");
[…]

### 2018-05-14 util/zkid_helpers.cpp

@@ -109,6 +109,7 @@ void ExportProof(LibsnarkCredentialProof &auth, std::string fname)
         std::cerr << "Could not open proof export file" << std::endl;
         return;
     }
+    
     f << "event Verified(string);" << std::endl;
     f << "function verifyTx() returns (bool r) {" << std::endl;
     f << "\tuint[] memory input = new uint[](" << auth.primary_input.size() << ");" << std::endl;

### 2018-05-14 src/network/ZkidService.cpp
Changed Credential to represent merkle path

@@ -91,6 +91,10 @@ bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_reque
         return false;
     }
 
+    for(auto node : merkle_path){
+        std::cout << node << std::endl;
+    }
+
     zkidProverImpl<sha256_two_to_one_hash_gadget> prover(merkle_path.size(), 32, _service_config->GetKeyPath());
 
     ProofRequest proof_request = ConstructProofRequest(cred_request, cred, merkle_root, merkle_path);

### 2018-05-14 src/ui/js/zkid.js

@@ -22,7 +22,8 @@ function ProofToBytes(proof) {
         web3.utils.hexToBytes(proof["H"][0]),
         web3.utils.hexToBytes(proof["H"][1]),
         web3.utils.hexToBytes(proof["K"][0]),
-        web3.utils.hexToBytes(proof["K"][1])), web3.utils.hexToBytes(proof["serial"]));
+        web3.utils.hexToBytes(proof["K"][1])), 
+        web3.utils.hexToBytes(proof["serial"]));
 }
 
 

### 2018-05-14 util/zkid_helpers.cpp
Change export format

@@ -38,12 +38,12 @@ VerificationKey ExtractVerificationKey(libsnark::r1cs_ppzksnark_verification_key
 
 std::string FormatG1(std::array<std::string, 2> p)
 {
-    return p[0] + ", " + p[1];
+  return "\"" + p[0]+"\"" + ", " + "\""+ p[1] + "\"";
 }
 
 std::string FormatG2(std::array<std::string, 4> p)
 {
-    return "[" + p[0] + ", " + p[1] + "], [" + p[2] + ", " + p[3] + "]";
+  return "\"" + p[0] + "\"" + ", " + "\"" + p[1] + "\"" + ", " + "\"" + p[2]+ "\"" + ", " + "\"" + p[3] + "\"";
 }
 
 void ExportVerificationKey(VerificationKey &vk, const std::string &sol_path, const std::string &out_path)
@@ -109,25 +109,20 @@ void ExportProof(LibsnarkCredentialProof &auth, std::string fname)
         std::cerr << "Could not open proof export file" << std::endl;
         return;
     }
-    f << "event Verified(string);" << std::endl;
-    f << "function verifyTx() returns (bool r) {" << std::endl;
-    f << "\tuint[] memory input = new uint[](" << auth.primary_input.size() << ");" << std::endl;
-    f << "\tProof memory proof;" << std::endl;
+    f << "["<< FormatG1(proof.A) << ", "
+      << FormatG1(proof.A_p) << ", "
+      << FormatG2(proof.B) << ", "
+      << FormatG1(proof.B_p) << ", "
+      << FormatG1(proof.C) << ", "
+      << FormatG1(proof.C_p) << ", "
+      << FormatG1(proof.H) << ", "
+      << FormatG1(proof.K) << "]" << std::endl << std::endl;
 
-    f << "\tproof.A = Pairing.G1Point(" << FormatG1(proof.A) << ");" << std::endl;
-    f << "\tproof.A_p = Pairing.G1Point(" << FormatG1(proof.A_p) << ");" << std::endl;
-    f << "\tproof.B = Pairing.G2Point(" << FormatG2(proof.B) << ");" << std::endl;
-    f << "\tproof.B_p = Pairing.G1Point(" << FormatG1(proof.B_p) << ");" << std::endl;
-    f << "\tproof.C = Pairing.G1Point(" << FormatG1(proof.C) << ");" << std::endl;
[…]

### 2018-05-14 src/network/ZkidService.cpp
Added proof

@@ -91,16 +91,13 @@ bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_reque
         return false;
     }
 
-    for(auto node : merkle_path){
-        std::cout << node << std::endl;
-    }
-
     zkidProverImpl<sha256_two_to_one_hash_gadget> prover(merkle_path.size(), 32, _service_config->GetKeyPath());
 
     ProofRequest proof_request = ConstructProofRequest(cred_request, cred, merkle_root, merkle_path);
     LibsnarkCredentialProof libsnark_data;
     if (prover.GetCredentialProof(proof_request, proof, libsnark_data))
     {
+        ExportProof(libsnark_data,"proof.temp");
         console->info("Successfully generated proof for: {0}", issuer_address);
         return true;
     }

### 2018-05-14 src/network/ZkidService.cpp
Contract Generation

@@ -98,6 +98,8 @@ bool ZkidService::GenerateProofForCredential(const CredentialRequest &cred_reque
     if (prover.GetCredentialProof(proof_request, proof, libsnark_data))
     {
         ExportProof(libsnark_data,"proof.temp");
+        VerificationKey key = ExtractVerificationKey(prover.GetVerificationKey());
+        ExportVerificationKey(key,"test/res/verification.sol.tmpl","verifier.sol");
         console->info("Successfully generated proof for: {0}", issuer_address);
         return true;
     }

### 2018-05-14 util/zkid_helpers.cpp

@@ -12,7 +12,7 @@ void ExtractCredentialProof(libsnark::r1cs_ppzksnark_proof<libff::alt_bn128_pp> 
     p.K = libsnark::outputPointG1AffineAsHex(proof.g_K);
 }
 
-VerificationKey ExtractVerificationKey(libsnark::r1cs_ppzksnark_verification_key<libff::alt_bn128_pp> &vk)
+VerificationKey ExtractVerificationKey(const libsnark::r1cs_ppzksnark_verification_key<libff::alt_bn128_pp> &vk)
 {
     VerificationKey k;
 

### 2018-05-14 util/zkid_helpers.h

@@ -19,7 +19,7 @@ struct LibsnarkCredentialProof
 
 void ExtractCredentialProof(libsnark::r1cs_ppzksnark_proof<libff::alt_bn128_pp> &proof, CredentialProof& cred_proof);
 
-VerificationKey ExtractVerificationKey(libsnark::r1cs_ppzksnark_verification_key<libff::alt_bn128_pp> &vk);
+VerificationKey ExtractVerificationKey(const libsnark::r1cs_ppzksnark_verification_key<libff::alt_bn128_pp> &vk);
 
 std::string FormatG1(std::array<std::string, 2> p);
 

### 2018-05-14 util/zkid_helpers.cpp
Chnage quoting

@@ -38,12 +38,12 @@ VerificationKey ExtractVerificationKey(libsnark::r1cs_ppzksnark_verification_key
 
 std::string FormatG1(std::array<std::string, 2> p)
 {
-  return "\"" + p[0]+"\"" + ", " + "\""+ p[1] + "\"";
+  return  p[0]+ ", " + p[1];
 }
 
 std::string FormatG2(std::array<std::string, 4> p)
 {
-  return "\"" + p[0] + "\"" + ", " + "\"" + p[1] + "\"" + ", " + "\"" + p[2]+ "\"" + ", " + "\"" + p[3] + "\"";
+  return  "[" + p[0] +  ", "  + p[1] + "], ["  + p[2] + ", "  + p[3]+"]";
 }
 
 void ExportVerificationKey(VerificationKey &vk, const std::string &sol_path, const std::string &out_path)

### 2018-05-14 paper/paper.tex
Add text

@@
 	anonymous credential scheme for the Ethereum blockchain and give
-	benchmarks for usage costs. We present as well an example application.
+	benchmarks for usage costs. We present as an example application an
+  age-verification contract.
 \end{abstract}
@@
 systems, they pose a challenge in that due to their public nature it is
-currently impossible to attest to aspects of one's identity without some
-trusted credential issuer.
+currently impossible to attest to aspects of one's identity without the
+participation of a trusted credential issuer. Many distributed applications have
+some responsibility to verify aspects of their users' identity, such as age or
+place of residence, but would ideally not reveal anything else about the user,
+including metadata about past and future attestations of identity.
 
@@
 
-\subsection{Implementation}
+\subsection{Approach}
 We implement zero-knowledge proofs using the elliptic curve pairing precompiled
@@
 
-\section{Properties and Features}
-Our zero-knowledge identity system allows for highly flexible ad-hoc issuance of
-credentials through \textit{k-show} credentials and range-bounded attributes.
-
-The public inputs are
-\begin{equation*}
-  \texttt{m\_root},\ \{l_1, \dots, l_7\},\ \{u_1, \dots, u_7\}, S, k
-\end{equation*}
-
-Each proof is an assertion that the prover holds a credential
-\begin{equation*}
-c = (sk, \{attr_1, \dots, attr_7\})  
-\end{equation*}
- such that
-
-\begin{enumerate}[1.]
-\item The credential is a leaf of a merkle tree with root \texttt{m\_root}.
-\item The credential contains some attributes $\{attr_1, \dots, attr_7\}$ with
-  $attr_i \in [l_i,u_i]$
-\item The credential has been used fewer than $k$ times with the salt $S$
-\end{enumerate}
-
 \section{Implementation}
@@
 \subsection{Credentials}
+
+\subsubsection{Credential Contents}
 Each credential is of the form
@@
 
-\subsection{Credential Requests}
+\subsubsection{Credential Requests}
 A credential request is a tuple of the form
 \begin{equation*}
-  r = (\texttt{merkle\_root}, \texttt{serial}, \{u_1, \dots,u_n\}, \{\ell_1,\dots,\ell_n\}, S, k)
+  r = (\texttt{merkle\_root}, \{u_1, \dots,u_n\}, \{\ell_1,\dots,\ell_n\}, S, k\_bound)
 \end{equation*}
@@
 commitments, $u_i, \ell_i \in \Z_{2^{32}}$ are bounds on acceptable attribute
-values, $S$ is a request-specific salt, and $k\in \N$ is the allowed number of
+values, $S$ is a request-specific salt, and $k\_bound\in \N$ is the allowed number of
 uses of a single credential per salt $S$.
 
-\subsection{k-show Credentials}
+\subsubsection{k-show Credentials}
 Every proof $\pi$ that a user generates has as public input
@@
 
-\subsection{Bounded-attributes}
+\subsubsection{Bounded-attributes}
 A proof for a given credential request $r$ must assert that $attr_i \in [\ell_i,
@@
 
-\subsection{Credential Scheme}
-verifier
+\subsubsection{Arithmetic Circuit}
+The verification algorithm for credentials is encoded as a rank-1 constraint
+system, and accepts as public input a credential request $r$ along with a serial
+number \texttt{serial}, and as private
+input
+\begin{equation*}
+  aux = (c, k, M)
+\end{equation*}
+where $c$ is the credential satisfying request $r$, $k$ is the nonce that
+generates $\texttt{serial}$, and $M$ is a merkle proof giving the authentication
+path for $c$. The circuit constrains
+\begin{itemize}
+\item $M$ to be a valid merkle proof for $c$ in
+  the tree with root $\texttt{merkle\_root}$
+\item $k \leq k\_bound$
+  \item  $\ell_i\leq
+    attr_i\leq u_i$
+  \item \texttt{serial} = $ H(\texttt{sk}_u || S_v || k)$
+\end{itemize}
+
+The verifier accepts if the proof satisfies this circuit and \texttt{serial} is
+not in its nullifier set $N$.
 

### 2019-01-16 paper/paper.tex

@@
 Identity systems for public blockchains have been proposed before in the form of
-serivces like Civic and Uport, wherein users can acquire attestations from
+serivces like Civic\cite{CivicSecureIdentity} and Uport\cite{braendgaardDifferentApproachesEthereum2018}, wherein users can acquire attestations from
 trusted issuers about facets of their identity (name, age, country of origin,
@@
 \subsection{The ZKID Service}
-
-\subsubsection{libsnark}
-
+\begin{figure}[h]
+  \centering
+  \includegraphics[scale=0.5]{issuing}\vspace{40pt}
+  \includegraphics[scale=0.5]{verifying}
+  \caption{ZKID Service}
+\end{figure}
 \subsubsection{JSON RPC}
@@
 
-\subsection{dApp Framework and Credential-Enabled Contracts}
-
-Add some Introduction here
-
 \subsubsection{Credential Annotated ABI}
@@
 
+Deployment of our contract takes $3.6$ million gas, and a single execution of
+the verifier requires $1.79$ million. At current prices this is about $0.01432$
+ETH or $\$10.50$. Proving time for a tree dept of $32$ is 43.2 seconds. We feel
+that these are reasonable enough for use, but could certainly be improved as
+discussed below. Proving time scales linearly with the depth of the merkle tree,
+while verification cost is constant.
+
 \section{Example Application}
@@
 \section{Future Work}
+Currently the contract does not make use of the preprocessed verifier that
+libsnark provides, which would allow us to remove 2 pairing checks at the cost
+of several EC group operations. Additionally, Zcash is developing a new zkSNARK
+system on a more efficient curve called JubJub\cite{ZcashJubjub} that allows fixed-base
+exponentiation for efficient EC operations in
+circuits, allowing efficient CRHs.
 
-\section{Conclusion}
+\section{Acknowledgements}
+Huge thanks to Ian Miers for helping set us on the right path and formalizing
+the properties that an anonymous credential scheme should have.
 
